---
title: "Data Wrangling Temp"
author: "Lauren Meyer"
date: "March 29, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(psych)
```

This file is not meant to be a final part, it's where I'm keeping the data wrangling code until we can incorporate it into the final paper. -Lauren

```{r }
dailydiary <- read_csv("TeleCom_Dyad_dailydiary.csv")
premeasures <- read_csv("TeleCom_Dyad_premeasures.csv")
#view(premeasures)

```



```{r, echo=FALSE}
#Simple helper function to convert "Yes" and "No" to 1 and 0 for summing
YesNo <- function(x){
    ifelse(x=="Yes", 1,0)
}

stripChars <- function(x) {
  parse_number(x)
}

reverseScale9 <- function(x) {
  1 + 9 - x
}

```

## Chores
For daily diaries chore level: Sum number of childcare tasks for each partner over all days. Keep dyad id, participant id, gender, and sum of tasks
to filter couples with no children, join to premeasures, check for numbers in people_4_TEXT and people_5_TEXT

```{r childcare}
filter_children <- premeasures %>%
  select(ResponseId, dyadID, people_4_TEXT, people_5_TEXT) %>%
  mutate(people_4_TEXT = ifelse(is.na(people_4_TEXT), 0, people_4_TEXT)) %>%
  mutate(people_5_TEXT = ifelse(is.na(people_5_TEXT), 0, people_5_TEXT)) %>%
  mutate(children = ifelse(people_4_TEXT > 0, 1, ifelse(people_5_TEXT > 0, 1, 0)), childnum = people_4_TEXT + people_5_TEXT, na.rm = TRUE) %>%
  select(ResponseId, children, childnum)

clean_dd <- dailydiary %>%
  select(partID, dyadID, gender, homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding) %>%
  mutate_at(vars(-partID, -dyadID, -gender),YesNo) %>%
  mutate_if(is.numeric, funs(ifelse(is.na(.), 0, .)))

chores_final <- inner_join(clean_dd, filter_children, by = c("partID" = "ResponseId")) %>%
  filter(children == 1) %>%
  mutate(total_chores = rowSums(across(c(homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding), na.rm = TRUE))) %>%
  group_by(partID) %>%
  summarize(total_chores = sum(total_chores))

rm(clean_dd)
```

## Self- and Other-objectification scores: 
Column variables correspond to the factors that are being ranked, the value is the rank of said factor. 

Scores should range from -25 to 25, with higher scores representing a greater focus on attractiveness and greater objectification. 

```{r self-objectification}
comp_v <- c(1,2,4,7,9)
attr_v <- c(3,5,6,8,10)
self_obj <- premeasures %>%
  select(ResponseId, dyadID, `self-object_1`, `self-object_2`, `self-object_3`, `self-object_4`, `self-object_5`, `self-object_6`, `self-object_7`, `self-object_8`, `self-object_9`, `self-object_10`) %>%
  mutate(comp = `self-object_1` + `self-object_2` + `self-object_4` + `self-object_7` + `self-object_9`, attr = `self-object_3` + `self-object_5` + `self-object_6` + `self-object_8` + `self-object_10`) %>%
  mutate(self_obj_score = comp - attr) %>%
  mutate(self_obj_score = ifelse(is.na(`self-object_1`), NA, self_obj_score)) 
#Confirming that they correlate at -1
corr.test(select(self_obj, comp, attr))
self_obj <- self_obj %>%
  select(ResponseId, dyadID, self_obj_score)
rm(comp_v, attr_v)
```

```{r other-objectification}
other_obj <- premeasures %>%
  select(ResponseId, dyadID, `other-object_1`, `other-object_2`, `other-object_3`, `other-object_4`, `other-object_5`, `other-object_6`, `other-object_7`, `other-object_8`, `other-object_9`, `other-object_10`) %>%
  mutate(comp = `other-object_1` + `other-object_2` + `other-object_4` + `other-object_7` + `other-object_9`, attr = `other-object_3` + `other-object_5` + `other-object_6` + `other-object_8` + `other-object_10`) %>%
  mutate(other_obj_score = comp - attr) %>%
  mutate(other_obj_score = ifelse(is.na(`other-object_1`), NA, other_obj_score)) 
corr.test(select(other_obj, comp, attr))
other_obj <- other_obj %>%
  select(ResponseId, other_obj_score)
```

```{r combined-objectification}
objectification <- inner_join(self_obj, other_obj, by = c("ResponseId" = "ResponseId")) 
temp_obj_1 <- objectification %>%
  #adding an alternating index for use in APIM calculations
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(self_obj_score_P1 = self_obj_score, other_obj_score_P1 = other_obj_score) %>%
  select(dyadID, ind, self_obj_score_P1, other_obj_score_P1)

temp_obj_2 <- objectification %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(self_obj_score_P2 = self_obj_score, other_obj_score_P2 = other_obj_score) %>%
  select(-ResponseId)

objectification <- objectification %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(temp_obj_1, by = c("dyadID", "ind")) %>%
  left_join(temp_obj_2, by = c("dyadID", "ind")) %>%
  mutate(self_obj_score_P = ifelse(is.na(self_obj_score_P1), self_obj_score_P2, self_obj_score_P1)) %>%
  mutate(other_obj_score_P = ifelse(is.na(other_obj_score_P1), other_obj_score_P2, other_obj_score_P1)) %>%
  select(ResponseId, dyadID, self_obj_score, other_obj_score, self_obj_score_P, other_obj_score_P)



rm(self_obj, other_obj, temp_obj_1, temp_obj_2)
```


## Relationship Quality

```{r relationship_quality}
rel_qual <- premeasures %>%
  select(ResponseId, dyadID, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars) %>%
  #These are the ones being reversed
  mutate_at(vars(relation_qual_2, relation_qual_4, relation_qual_7, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_18, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24), reverseScale9)

corr.test(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))$r
#23 might be worth dropping, but the alpha is high enough (0.9) that we don't *need* to drop anything
alpha(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))

#Final calculation
rel_qual$total_relation_qual <- rowMeans(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25), na.rm = TRUE)
rel_qual <- rel_qual %>%
  select(ResponseId, dyadID, total_relation_qual)
```

# Gatekeeping premeasures
```{r gatekeeping}
gatekeep <- premeasures %>%
  select(ResponseId, dyadID, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars)

corr.test(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#looking good, nothing needs to be reversed

alpha(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#.92 alpha, nothing that looks like it needs reversing

gatekeep$gatekeep_total <- rowMeans(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15), na.rm = TRUE)

gatekeep <- gatekeep %>% 
  select(ResponseId, dyadID, gatekeep_total)
```

## Gatekeeping DailyDiaries

```{r gatekeeping_2}
scaleToNumeric <- function(x) {
  ifelse(x == "Strongly agree", 5, ifelse(x == "Somewhat agree", 4, ifelse(x == "Neither agree nor disagree", 3, ifelse(x == "Somewhat disagree", 2, ifelse(x == "Strongly disagree", 1, NA)))))
}

dd_gatekeep <- dailydiary %>%
  select(partID, dyadID, gate1, gate2, gate3, gate4, gate5, gate6) %>%
  mutate_at(vars(gate1, gate2, gate3, gate4, gate5, gate6), scaleToNumeric)

corr.test(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#no negative correlations again! we good.

alpha(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#alpha of 0.84. Just fine. 1 and 4 could get dropped but it's consistent enough as is. 

dd_gatekeep$gateTotal <- rowMeans(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6), na.rm = TRUE)
dd_gatekeep <- dd_gatekeep %>%
  group_by(partID) %>%
  summarize(dd_gateTotal = mean(gateTotal))
```

## Final assembled dataset
Work in progress as I add more variables
Also note that there are about 100 people who did not fill out the daily diaries. 

```{r dataset_assembly}
assembled_dataset <- premeasures %>%
  select(ResponseId, dyadID, gender, race, Q139) %>%
  inner_join(., objectification) %>%
  inner_join(., rel_qual) %>%
  rename(relation_qual = total_relation_qual) %>%
  left_join(., gatekeep) %>%
  rename(gatekeep_premeasures = gatekeep_total) %>%
  left_join(dd_gatekeep, by = c("ResponseId" = "partID")) %>%
  rename(gatekeep_diaries = dd_gateTotal) %>%
  left_join(chores_final, by = c("ResponseId" = "partID")) %>%
  rename(childcare_tasks = total_chores) %>%
  left_join(filter_children) %>%
  rename(children_any = children) %>%
  rename(teleworking = Q139)

#cleanup
rm(objectification, rel_qual, gatekeep, dd_gatekeep, chores_final, filter_children)
```


## Childcare percent

```{r cc_percent}
total_childcare_temp <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  group_by(dyadID) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  summarize(total_tasks = sum(childcare_tasks)) %>%
  filter(total_tasks > 0)

childcare_temp2 <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  left_join(total_childcare_temp) %>%
  filter(total_tasks > 0) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  mutate(childcare_percent = childcare_tasks / total_tasks * 100) %>%
  select(ResponseId, childcare_percent)

assembled_dataset <- assembled_dataset %>%
  left_join(childcare_temp2)

#cleanup
rm(total_childcare_temp, childcare_temp2)
```

```{r children_discrep}

#Initial Corrections: 
#The number of children entered by R_3Jgt1VbMKwbyTKE seems to be a typo, entered 10, partner put 0. 
assembled_dataset <- assembled_dataset %>%
  mutate(childnum = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, childnum), children_any = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, children_any))


children <- assembled_dataset %>%
  select(ResponseId, dyadID, children_any, childnum) %>%
  group_by(dyadID)

maxchildren <- children %>%
  summarize(children_max = max(childnum))

children_discrep <- children %>%
  left_join(maxchildren) %>%
  mutate(child_diff = children_max - childnum) %>%
  filter(child_diff > 0)
#there were 18 respondents who reported fewer children than their partners. 

rm(maxchildren, children)
```


```{r}
same_sex <- assembled_dataset %>%
  mutate(gender = ifelse(gender == "Man", 0, 1)) %>%
  group_by(dyadID) %>%
  summarize(couple = sum(gender)) %>%
  mutate(couple = ifelse(couple == 0, "Same-sex Male", ifelse(couple == 1, "Different-sex", "Same-sex Female")))
assembled_dataset <- assembled_dataset %>%
  left_join(same_sex, by = "dyadID") %>%
  rename(couple_genders = couple)


same_race <- assembled_dataset %>%
  group_by(dyadID, race) %>%
  summarize(n = n()) %>%
  mutate(couple_race = ifelse(n == 2, "Same Race", "Mixed Race")) %>%
  select(dyadID, couple_race) %>%
  distinct()
assembled_dataset <- assembled_dataset %>%
  left_join(same_race, by = c("dyadID" = "dyadID"))

```


```{r rel_lengths}
getYear <- function(x){
  parse_number(substr(x, nchar(x)-1, nchar(x)))
}
last_year_parsed <- premeasures %>%
  select(ResponseId, dyadID, relation_length, married, marriage_length) %>%
  #Parsing to the year number
  mutate(relation_length = getYear(relation_length), marriage_length = getYear(marriage_length)) %>%
  mutate(relation_length = (120 - relation_length) %% 100, marriage_length = (120 - marriage_length) %% 100) %>%
  select(-dyadID)
#Note: dyad 7403083 looks incredibly fucky. They don't agree whether they're married, disagree on relationship length by five years, and claim to have 33 children. ????


assembled_dataset <- assembled_dataset %>%
  left_join(last_year_parsed)
```
