---
title             : "dicussion"
shorttitle        : "Syrine, lauren, angela"

author: 

  - name          : "Syrine, lauren, angela"
    # affiliation   : "1"
    role:


affiliation:
  - id            : " "
    institution   : "Smith College"



abstract: | 
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "annotated.bib"]
nocite            : |
  @RadcliffeL, @SweeneyK, @BleskeRechekA, @MeierJ, @CarlsonDDivision, @CarlsonDFathers, @NewkirkK, @DelBocaD, @CrosbieT, @ChungH

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Discussion:

The present study is the first to examine the relationship between objectification and childcare labor in cohabitating relationships. Objectification Theory [@FredrickB] has advanced our understanding of the negative mental health outcomes of self-objectification [@MercurioA; @BrockR] and has provided a framework for understanding how self-objectification might negatively affect women’s participation in gender-based activism [@CalogeroR] and their relationship satisfaction [@DownsD ; @ZurbriggenE] The present study builds on the existing literature of self-objectification by providing evidence that self-objectification is an important predictor of childcare task division in a couple in that individuals who objectify themeselves more end up doing more childcare tasks. Partner-objectification is only a predictor of childcare when controlling for the gender interaction effect in that higher partner-objectification for women lowers childcare. The findings also provide evidence that gender role adherence is not a factor for relationship satisfaction for fathers performing childcare. This contradicts the popular view that fathers feel dissatisfaction or resentment when diverging from the traditional gender role that assign women the bulk of childcare. 


Our hypothesis that fathers who do a larger share of the childcare labor tasks would feel resentment toward their partners and subsequently feel less satisfied in their relationship, was not supported. We did not find any evidence that childcare affected fathers' relationship satisfaction/fulfilment. Although [@NewkirkK] found that childcare did not affect conflict for fathers, our results are still surprising given that [@CarlsonDDivision] showed that fathers who took on a higher load of childcare then their partner, had slightly lower sexual relationship quality. Gatekeeping was not a significant moderator for childcare and realtionship satisfaction. This was unexpected given that [@AllenS] proved that gatekeepers performed more childcare. We suspect that the lack of significance may be due to our sample considerably decreasing by 60% after ommiting couples who didn't have children and had were missing crucial data, and our observations decreasing by 50% after limiting the our first hyppothesis analysis to fathers. Furthermore, when fathers gatekeep or their partner gate keeps it doesn't affect how satisfied they feel in their relationship or much childcare they do which is inconstistant with [@AllenS] findings that demonstrated that gatekeepers performed more chilcare.

Our hypothesis that individuals with partner who highly objectified them would take on a smaller role in caring for their children was not supported. More specifically, when an individual's partner objectified them more it did not affect the amount of childcare they performed. Given that self-objectification signifcantly affected childcare tasks and that objectification is self-perpetuating in that people who are objectified by others tend to self-objectify [@StrelanP; @ZurbriggenE], we expect that the lack of significance in our results may be due to the non-independence between self objectification and partner objectification in the sense that partner objectification directly affected self objectification rather than affecting childacre tasks. 

Our hypothesis that individuals who objectified themselves more would take on a larger role in caring for their children was supported. More specifically, individuals who put higher emphasis on their physical traits tend to perform more childcare tasks. We speculated that this may be due to the fact that people who self-objectify tend to perform more service tasks because they view themselves as vessels[@FredrickB]. As expected, we found that women took on a higher load of childare tasks than men in general which is consistent with  [@RhoadsS] findings. We expect these result to be due to US societal norms that place mothers as the primary caretaker of children [@RadcliffeL; @BroseS]. However conrtrary to our expectations mother's load of childcare tasks decreased when their partner objectified them more. A possible explanation may be that individuals who objectify their partners, also idoliaze them and as a result help them with time-consuming, menial tasks like childcare. We hope to explore this relationship in the future. 

# Limitations and Future Directions:

The current study is limited in several ways. First, we were unable to test our first hypothesis(relationship between childcare and relationship satisfcation) with same-sex dyads or inlcluded multilevel and APIM dyadic anlaysis, because of our sample did not include any same-sex male couples with children. Since childcare is affected by societal norms that place mothers as the primary caretaker of children [@RadcliffeL; @BroseS], future work should examine childcare and relationship satisfcation in lgbtq+ communities/couples with alternative gender norms. We measured parent's gender effect on childcare but not the children's gender effect because information about children's gender was not collected in this study. Future research can measure the effect of both the parents' and children's gender on the parents' childcare tasks and test the factuality of the stereotypes around gender-based parent favoritsm like "mama's boy" or "dady's girl". Due to the inexpected results of our third hypothesis showing that mothers' childcare is when their partner objectified them more we think future study should explore  the effect of idividuals(or men's) partner-objectification on their idiolization and expections of their partner.


In addition our sample size was reduced from 182 couples to 71 couples after ommiting couples who didn't have children and were missing crucial data, and our observations decreasing by 50% due to our focus on father in the first questions. We suspect that these reasons contributed to the lack of statistically significant results for the first and third hypotheses. Our predictory measures were based on self-reports in daily diaries and premeasures. We suspect, that childcare reports had many missing values because parents sometimes forgot to report their tasks diaries which might affect the accuracy of our results. Because the majority of our couples were white, same-race, heterosexual, and teleworking, our findings can be generalized to the entire population. Because our study was conducted during the COVID-19 pandemic when fathers working from home had spent more time caring for their children [@CarlsonD; @ChungH], it may not capture the general childcare dynamics in a couple pre and post pandemic. 



# State the final conclusions/implications that your research has for society:

Our study generated several important insights(first, our finding that .. suggests that .. ). (Even through an extensive amount of research has examined the effects of objectification on the mental health and self-esteem of a person, to the best of our knowlege MYABE DELETE?), our study is the first to shed light on the dynamics to assess the importance/effect of objectification on the childcare division dynamics in a dyadic framework of cohabiting couples. Since couples reported better relationship quality and lower conflict when the division of household tasks was equitable [@CarlsonD; @NewkirkK], our findings have implications for practicioners seeking to help couples improve their coparenting, reduce their conflicts, and improve relationship qulaity by taking into account high self-objectifcation a contributor in the unequal division of childcare. 

## Data analysis
We used `r cite_r("r-references.bib")` for our analysis.


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup


