---
title             : "dicussion"
shorttitle        : "Syrine, lauren, angela"

author: 

  - name          : "Syrine, lauren, angela"
    # affiliation   : "1"
    role:


affiliation:
  - id            : " "
    institution   : "Smith College"



abstract: | 
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "annotated.bib"]
nocite            : |
  @RadcliffeL, @SweeneyK, @BleskeRechekA, @MeierJ, @CarlsonDDivision, @CarlsonDFathers, @NewkirkK, @DelBocaD, @CrosbieT, @ChungH

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Discussion:

Several studies examined the effects of objectification on mental health, self-esteem, gender-related social activism, and realationship satisfaction. These studies have demonstarated that partner objectification can lead to lower relationship satisfaction [@RamseyL] and self-objectification can lead to negative body image, body shame, lower self-esteem, and mental health disorderslike disordered eating, diminished cognitive capacity, and self-harm [@MercurioA], [@FredrickB]. It can also lower women's relationship satisfcation [@DownsD], [@ZurbriggenE] and disrupt their social activism [@CalogeroR]. However, to the best of our knowlege, this is the first study to investigate the role of objectification on the division of childcare in a couple. Given our findings we can assert that unlike partner-objectification, self-objectification is an important predictor of childcare task division in a couple in that individuals who objectify themeselves more end up doing more childcare tasks. We also found that childcare is not a factor that affects fathers relationship satifcation. This contradicts the popular view that fathers feel dissatistfaction or resentment when diverging from the traditional gender role that assign women the bulk of childcare. 

Our hypothesis that fathers who do a larger share of the childcare labor tasks would feel resentment toward their partners and subsequently feel less satisfied in their relationship, was not supported. We did not find any evidence that childcare affected fathers' relationship satisfaction/fulfilment. Although [@NewkirkK] found that childcare did not affect conflict for fathers, our results are still surprising given that [@CarlsonDDivision] showed thatfathers who took on a higher load of childcare then their partner, had slightly lower sexual relationship quality. Gatekeeping was not a strong moderator for childcare and realtion satisfaction. This was unexpected given that [@AllenS] proved that gatekeepers performed more childcare. We suspect that the lack of significance may be due to our sample considerably decreasing by 60% after ommiting couples who didn't have children and had were missing crucial data, and our observations decreasing by 50% after limiting the our first hyppothesis analysis to fathers. Furthermore, when fathers gatekeep or their partner gate keeps it doesn't affect how satisfied they feel in their relationship or much childcare they do.

Our hypothesis that individuals who objectified themselves more would take on a larger role in caring for their children was supported. More specifically, individuals who value their physical attributes more than their personality/view themeslevs as objects tend to perform more childcare tasks. We speculated that this may be due to the fact that people who self-objectify tend to perform more service tasks because they view themselves as vessels/objects (if we can find something similar). As expected, we found that women took on a higher load of childare tasks in general which adheres to traditional gender role site other studies related. However conrtrary to our expectations their childcare decreased when their partner objectified them more. A possible explanation may be that individuals who objectify their partners, also idoliaze them and as a result help them with time-consuming tasks like childcare. We hope to explore this relationship in the future. 

Our hypothesis that individuals with partner who highly objectified them would take on a smaller role in caring for their children was not supported. More specifically, when a individual's partner objectified them more it didn't affect the amount of childcare they performed. average self-objetification is lower for lower than it wasn't enough to have an effect. self objection and partner objectification affected self objectification had a direct relation wich maybe partner objectification affected self rather than tasks site related studies.

# Limitations:

In our first research question, we hoped to be able to see the effect of childcare on father's relationships in both same-sex and heterosexual couples. However, the majority of couples in our samples were heterosexual and of the 3 same sex male couples none had children(double check). Therefore we were unable to assess the previously stated relationship for same sex male couples or to use dyadic data analysis.
In addition our sample size was reduced from 182 couples to 71 couples and observations was cut by half due to our focus on father in the first questions. We suspect that these reasons might contribute to the lack of statistically significant results for the first and third hypotheses.
For mothers, the relationship was linear meaning the more
their partners were involved,
didn't have gender of children gatekeeping site crap:"(
Finally, we noticed that missing data in the pre-measure and diary. Our predictory measure were based on self-reports and we suspect that many partcipants forgot to fill in their diaries which might affect the accuracy of our results.
we dont know how representative because sample was majority white same race heterosexual and during covid working from how affect chioldcare job siye how job affects parent childcare.

# Consider any future research studies that could be done given new questions your study raises

In our analysis, we measured the effect on parent's gender on gatekeeping. For our future direction, we think it would be valuable to investigate the relationship between gatekeeping and gender of of children. Steretypical '', ''

- According to the results of our second hypothesis, we want to investigate the effect of partner-objectififcation on how much the indidual idiolizing/ expections of partner.

- assess test the first questions for same sex male couples. previous litterature talks about childcare is considered women's role, same sex couples go out of effect of tradition gender role adherence changes with self objectififcation in mind. adoptive parents

# State the final conclusions/implications that your research has for society:

Even through an extensive amount of research has examined the effects of objectification on the mental health and self-esteem of a person, to the best of our knowlege, this is the first
study to investigate the role of objectification on childcare in a couple/ relationship satisfaction. borader knowlege not just on mental health and feelings but actions and unequal divison of childcare between couple. this thing confirm the effect, self-objectification and adherence to gender roles. state other research
Sullivan, Billari, and Altintas (2014) This article gives additional evidence
that gendered preferences for childcare are largely shaped by society and can be changed; the
societal role of gendered norms inspired us when forming our first research question.

## Data analysis
We used `r cite_r("r-references.bib")` for our analysis.


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup


