---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

abstract: |
  The current study is the first to examine the relationship between objectification and childcare labor. Dyadic couples (n=71; 70 heterosexual and 1 same-sex) completed pre-measure surveys, then daily diaries for 14 days. Actor Partner Independence Modeling analysis found that people who self-objectified performed more childcare labor tasks. Partner-objectification and the role of childcare labor on father relationship satisfaction were also assessed. Findings provide further insight into the effects of objectification on romantic relationships. Implications for the future direction of objectification research are discussed.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "paper-references.bib", "annotated.bib"]
nocite            : |
  @CarlsonDDivision, @RhoadsS, @StrelanP, @ZurbriggenE, @RamseyL, @NewkirkK, @ChungH, @BleskeRechekA, @RhoadsS, @RadcliffeL, @ChickK, @BroseS, @SullivanO, @CraigL, @IshiiM, @WangR, @CarlsonD, @ChungH, @BjarnasonT, @DownsD, @RamseyL, @MaharE, @BrockR, @MercurioA, @CalogeroR, @FredrickB

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(mosaic)
library(lubridate)
library(nlme)
library(dplyr)
library(tidyverse)
library(readr)
library(psych)
library(kableExtra)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


Equitable division of childcare labor increases relationship satisfaction in cohabiting couples [@CarlsonDDivision]. Conversely, partner-objectification (viewing one's partner as an object) decreases relationship satisfaction for both men and women [@StrelanP; @ZurbriggenE] via self-objectification (viewing oneself as an object). [@RamseyL]. Objectification theory states that people who other-objectify in relationships tend to dehumanize their partners [@FredrickB]. Because childcare is considered a service task, the aim of the current study was to examine how the dynamic of objectification between partners affects the division of childcare labor in a dyadic framework of cohabiting couples.       
    Mothers continue to take on a larger share of childcare labor, even in dual-earning households [@RhoadsS]. Factors that may prevent fathers from becoming more involved with childcare include traditional gender-oriented attitudes regarding childcare labor [@BroseS; @RadcliffeL] and maternal gatekeeping [@AllenS]. We sought to understand if men who act counter to societal gender norms by performing a majority of the childcare tasks would experience reduced relationship satisfaction. Although societal attitudes shaping traditional gender roles position childcare as women's work [@BroseS; @ChickK], both men and women are affected by objectification [@BrockR; @MercurioA; @ZurbriggenE]. Because objectification is associated with dehumanization [@FredrickB], we sought to understand how objectification affects the division of service-oriented tasks in cohabitating relationships. To our knowledge, this is the first study to examine associations between objectification and childcare labor roles. The current study looks to broaden the academic literature on objectification by examining if partner-objectification and self-objectification influence the distribution of childcare labor tasks. 
  
**Childcare labor and gender roles**  
Cohabitating couples report less relationship conflict and higher relationship quality when the division of childcare labor is equitable [@CarlsonDDivision; @NewkirkK]. Despite this, women generally take on a larger share of childcare tasks than men [@BleskeRechekA; @ChungH], even when both partners have similar work obligations. In a study that examined married couples in which both partners were tenure track professors, fathers performed fewer childcare tasks than mothers, even when fathers held an egalitarian attitude toward childcare labor [@RhoadsS].  
  Although women reported enjoying childcare tasks more than men [@BleskeRechekA], this may be due more to societal expectations that position women as the primary caretaker of children [@RadcliffeL] rather than a biological drive. Socialization of gender roles begins in infancy, with boys and girls receiving different gendered messaging from caretakers. Boys receive more attention from daycare workers and are more likely to receive comments about their size and physical abilities, while girls are more likely to be reinforced for their appearance and helping behaviors [@ChickK]. These types of messages teach young children that a girl’s role is oriented toward domestic work [@ChickK] while boys are better suited for labor. In one study, most adolescents chose the mother as the parent who should stay home to care for children in equal earning couples, citing women’s social role as caretakers as a primary reason [@BroseS].  
  However, gender normative views on childcare might not be static. Very low fertility countries that have recently seen an increase in fertility rates, such as Germany and Slovenia, also saw an increase in childcare labor contributions from young, more highly educated fathers [@SullivanO]. These countries also saw a corresponding decline in the percentage of men agreeing with the statement, “A man’s job is to earn money; a woman’s job is to look after the home and family” [@SullivanO], suggesting social diffusion of a change in attitudes toward gender roles and domestic labor. Additionally, men with higher levels of education [@CraigL; @SullivanO], lower levels of work-related stress [@IshiiM], and more family-oriented work environments [@IshiiM] are more likely to be involved in childcare labor.   
  As mothers’ participation in the workforce has increased, so has fathers’ involvement in childcare labor [@WangR]. Recently, fathers who have transitioned to work-from-home positions due to restrictions from the Covid-19 pandemic have increased the amount of time spent taking care of children [@CarlsonD; @ChungH]. While couples reported better relationship quality when fathers were involved in childcare [@CarlsonD], and men reported higher relationship satisfaction when the division of household tasks was equitable [@CarlsonD], men who spent more time on childcare tasks than their partner experienced reduced sexual satisfaction in their relationships [@CarlsonD]. Along this vein, we predicted that men who go against traditional gender roles by performing a larger share of childcare labor than their partners would experience lower relationship satisfaction. 

**Objectification and Relationships**  
Objectification involves treating a person as an object rather than a being with thoughts and feelings [@FredrickB]. Higher levels of objectification in the context of a romantic relationship may harm relationship quality for both the person being objectified and the objectifier [@DownsD; @MaharE; @StrelanP; @RamseyL; @ZurbriggenE]. People who were objectified by their partner reported less satisfaction in their relationships [@DownsD; @ZurbriggenE]. Additionally, people who objectified their partner reported reduced relationship satisfaction [@ZurbriggenE], although one study found support for this only with women who objectified their partner [@MaharE]. Some aspects of objectification appear to affect men and women differently. One study found evidence that women who self-objectify are more likely to support and justify gender norms that support sexist ideologies. These women were less likely to engage in social activism centered on gender inequalities [@CalogeroR]. However, a subsequent study failed to replicate these findings [@DewildeM]. Men were more likely to objectify their partner than women. Additionally, men who engaged in objectification reported less relationship commitment and were more likely to believe they had higher-quality relationship alternatives [@MaharE]. Lower sexual satisfaction was also associated with both partner- and self-objectification in men [@ZurbriggenE]. However, there were no differences in self-objectification between men and women [@ZurbriggenE], and lower partner objectification was associated with increased sexual satisfaction in both men and women [@BrockR].  
  There is evidence that objectification has implications on personal well-being. Self-objectification has been associated with lower life satisfaction [@MercurioA], although research is mixed. Predicted associations between self-objectification and reduced self-esteem have been supported; however, there is no consensus about the link between self-objectification and body-esteem [@MercurioA; @StrelanP]. The absence of objectification predicted slightly more positive outcomes; in a study examining pregnant women and objectification, both men and women who felt humanized by their partner reported fewer depression symptoms [@BrockR].   
 	Partner- and self-objectification seem to be linked and self-perpetuating. People who other- and self-objectify are more likely to be in relationships with partners who also other- and self-objectify. Additionally, the more that someone is objectified, the more likely they are to self-objectify, which makes them more likely to objectify others [@StrelanP; @ZurbriggenE]. One study found that heterosexual women who enjoy being sexualized are more likely to feel objectified by their partner, leading to lower relationship satisfaction via increased self-objectification [@RamseyL]. Another study found that exotic dancers, sexualized by trade, reported feeling objectified more and having lower relationship satisfaction than college women; however, when moderated for sexual orientation, both college women and heterosexual exotic dancers had higher levels of relationship satisfaction than bisexual dancers [@DownsD].  
	The current research sought to expand on previous literature by examining the association between objectification and childcare labor. We predicted that partner-objectification would predict a lower contribution to childcare labor, while self-objectification would predict a higher contribution for both men and women. 

# Methods
```{r include = FALSE, echo=FALSE}

dailydiary <- read_csv("TeleCom_Dyad_dailydiary.csv")
premeasures <- read_csv("TeleCom_Dyad_premeasures.csv")
#view(premeasures)

#Simple helper function to convert "Yes" and "No" to 1 and 0 for summing
YesNo <- function(x){
    ifelse(x=="Yes", 1,0)
}

stripChars <- function(x) {
  parse_number(x)
}

reverseScale9 <- function(x) {
  1 + 9 - x
}

reverseScale6 <- function(x) {
  7 - x
}


### Basic Data Cleaning, Chores Calculations

filter_children <- premeasures %>%
  select(ResponseId, dyadID, people_4_TEXT, people_5_TEXT) %>%
  mutate(people_4_TEXT = ifelse(is.na(people_4_TEXT), 0, people_4_TEXT)) %>%
  mutate(people_5_TEXT = ifelse(is.na(people_5_TEXT), 0, people_5_TEXT)) %>%
  mutate(children = ifelse(people_4_TEXT > 0, 1, ifelse(people_5_TEXT > 0, 1, 0)), childnum = people_4_TEXT + people_5_TEXT, na.rm = TRUE) %>%
  select(ResponseId, children, childnum)

clean_dd <- dailydiary %>%
  select(partID, dyadID, gender, homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding) %>%
  mutate_at(vars(-partID, -dyadID, -gender),YesNo) %>%
  mutate_if(is.numeric, funs(ifelse(is.na(.), 0, .)))

chores_final <- inner_join(clean_dd, filter_children, by = c("partID" = "ResponseId")) %>%
  filter(children == 1) %>%
  mutate(total_chores = rowSums(across(c(homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding), na.rm = TRUE))) %>%
  group_by(partID) %>%
  summarize(total_chores = sum(total_chores))

rm(clean_dd)


### Self and Other Objectification Calculations

comp_v <- c(1,2,4,7,9)
attr_v <- c(3,5,6,8,10)
self_obj <- premeasures %>%
  select(ResponseId, dyadID, `self-object_1`, `self-object_2`, `self-object_3`, `self-object_4`, `self-object_5`, `self-object_6`, `self-object_7`, `self-object_8`, `self-object_9`, `self-object_10`) %>%
  mutate(comp = `self-object_1` + `self-object_2` + `self-object_4` + `self-object_7` + `self-object_9`, attr = `self-object_3` + `self-object_5` + `self-object_6` + `self-object_8` + `self-object_10`) %>%
  mutate(self_obj_score = comp - attr) %>%
  mutate(self_obj_score = ifelse(is.na(`self-object_1`), NA, self_obj_score)) 
#Confirming that they correlate at -1
corr.test(select(self_obj, comp, attr))
self_obj <- self_obj %>%
  select(ResponseId, dyadID, self_obj_score)
rm(comp_v, attr_v)

other_obj <- premeasures %>%
  select(ResponseId, dyadID, `other-object_1`, `other-object_2`, `other-object_3`, `other-object_4`, `other-object_5`, `other-object_6`, `other-object_7`, `other-object_8`, `other-object_9`, `other-object_10`) %>%
  mutate(comp = `other-object_1` + `other-object_2` + `other-object_4` + `other-object_7` + `other-object_9`, attr = `other-object_3` + `other-object_5` + `other-object_6` + `other-object_8` + `other-object_10`) %>%
  mutate(other_obj_score = comp - attr) %>%
  mutate(other_obj_score = ifelse(is.na(`other-object_1`), NA, other_obj_score)) 
corr.test(select(other_obj, comp, attr))
other_obj <- other_obj %>%
  select(ResponseId, other_obj_score)

objectification <- inner_join(self_obj, other_obj, by = c("ResponseId" = "ResponseId")) 
temp_obj_1 <- objectification %>%
  #adding an alternating index for use in APIM calculations
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(self_obj_score_P1 = self_obj_score, other_obj_score_P1 = other_obj_score) %>%
  select(dyadID, ind, self_obj_score_P1, other_obj_score_P1)

temp_obj_2 <- objectification %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(self_obj_score_P2 = self_obj_score, other_obj_score_P2 = other_obj_score) %>%
  select(-ResponseId)

objectification <- objectification %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(temp_obj_1, by = c("dyadID", "ind")) %>%
  left_join(temp_obj_2, by = c("dyadID", "ind")) %>%
  mutate(self_obj_score_P = ifelse(is.na(self_obj_score_P1), self_obj_score_P2, self_obj_score_P1)) %>%
  mutate(other_obj_score_P = ifelse(is.na(other_obj_score_P1), other_obj_score_P2, other_obj_score_P1)) %>%
  select(ResponseId, dyadID, self_obj_score, other_obj_score, self_obj_score_P, other_obj_score_P)



rm(self_obj, other_obj, temp_obj_1, temp_obj_2)

### Relationship Satisfaction Calculations and Alpha

rel_qual <- premeasures %>%
  select(ResponseId, dyadID, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars) %>%
  #These are the ones being reversed
  mutate_at(vars(relation_qual_2, relation_qual_4, relation_qual_7, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_18, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24), reverseScale9)

corr.test(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))$r
#23 might be worth dropping, but the alpha is high enough (0.9) that we don't *need* to drop anything
alpha(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))

#Final calculation
rel_qual$total_relation_qual <- rowMeans(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25), na.rm = TRUE)
rel_qual <- rel_qual %>%
  select(ResponseId, dyadID, total_relation_qual)


### Gatekeeping Calculations and Alpha

gatekeep <- premeasures %>%
  select(ResponseId, dyadID, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars)

corr.test(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#looking good, nothing needs to be reversed

alpha(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#.92 alpha, nothing that looks like it needs reversing

gatekeep$gatekeep_total <- rowMeans(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15), na.rm = TRUE)

gatekeep <- gatekeep %>% 
  select(ResponseId, dyadID, gatekeep_total)

scaleToNumeric <- function(x) {
  ifelse(x == "Strongly agree", 5, ifelse(x == "Somewhat agree", 4, ifelse(x == "Neither agree nor disagree", 3, ifelse(x == "Somewhat disagree", 2, ifelse(x == "Strongly disagree", 1, NA)))))
}

dd_gatekeep <- dailydiary %>%
  select(partID, dyadID, gate1, gate2, gate3, gate4, gate5, gate6) %>%
  mutate_at(vars(gate1, gate2, gate3, gate4, gate5, gate6), scaleToNumeric)

corr.test(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#no negative correlations again! we good.

alpha(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#alpha of 0.84. Just fine. 1 and 4 could get dropped but it's consistent enough as is. 

dd_gatekeep$gateTotal <- rowMeans(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6), na.rm = TRUE)
dd_gatekeep <- dd_gatekeep %>%
  group_by(partID) %>%
  summarize(dd_gateTotal = mean(gateTotal))

### Assembling the tables together

assembled_dataset <- premeasures %>%
  select(ResponseId, dyadID, gender, race, Q139) %>%
  inner_join(., objectification) %>%
  inner_join(., rel_qual) %>%
  rename(relation_qual = total_relation_qual) %>%
  left_join(., gatekeep) %>%
  rename(gatekeep_premeasures = gatekeep_total) %>%
  left_join(dd_gatekeep, by = c("ResponseId" = "partID")) %>%
  rename(gatekeep_diaries = dd_gateTotal) %>%
  left_join(chores_final, by = c("ResponseId" = "partID")) %>%
  rename(childcare_tasks = total_chores) %>%
  left_join(filter_children) %>%
  rename(children_any = children) %>%
  rename(teleworking = Q139)

#cleanup
rm(objectification, rel_qual, gatekeep, dd_gatekeep, chores_final, filter_children)

total_childcare_temp <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  group_by(dyadID) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  summarize(total_tasks = sum(childcare_tasks)) %>%
  filter(total_tasks > 0)

childcare_temp2 <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  left_join(total_childcare_temp) %>%
  filter(total_tasks > 0) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  mutate(childcare_percent = childcare_tasks / total_tasks * 100) %>%
  select(ResponseId, childcare_percent)

assembled_dataset <- assembled_dataset %>%
  left_join(childcare_temp2)

#cleanup
rm(total_childcare_temp, childcare_temp2)

### Calculating the existence and number of children, and the number of discrepencies

#Initial Corrections: 
#The number of children entered by R_3Jgt1VbMKwbyTKE seems to be a typo, entered 10, partner put 0. 
assembled_dataset <- assembled_dataset %>%
  mutate(childnum = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, childnum), children_any = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, children_any))


children <- assembled_dataset %>%
  select(ResponseId, dyadID, children_any, childnum) %>%
  group_by(dyadID)

maxchildren <- children %>%
  summarize(children_max = max(childnum))

children_discrep <- children %>%
  left_join(maxchildren) %>%
  mutate(child_diff = children_max - childnum) %>%
  filter(child_diff > 0)
#there were 18 respondents who reported fewer children than their partners. 

rm(maxchildren, children)

### Same Sex Relationship and Same Race Relationship markers

same_sex <- assembled_dataset %>%
  mutate(gender = ifelse(gender == "Man", 0, 1)) %>%
  group_by(dyadID) %>%
  summarize(couple = sum(gender)) %>%
  mutate(couple = ifelse(couple == 0, "Same-sex Male", ifelse(couple == 1, "Different-sex", "Same-sex Female")))
assembled_dataset <- assembled_dataset %>%
  left_join(same_sex, by = "dyadID") %>%
  rename(couple_genders = couple)


same_race <- assembled_dataset %>%
  group_by(dyadID, race) %>%
  summarize(n = n()) %>%
  mutate(couple_race = ifelse(n == 2, "Same Race", "Mixed Race")) %>%
  select(dyadID, couple_race) %>%
  distinct()
assembled_dataset <- assembled_dataset %>%
  left_join(same_race, by = c("dyadID" = "dyadID"))


### Marriage and Relationship Lengths, in years. Did not resolve disagreements. 

getYear <- function(x){
  parse_number(substr(x, nchar(x)-1, nchar(x)))
}
last_year_parsed <- premeasures %>%
  select(ResponseId, dyadID, relation_length, married, marriage_length) %>%
  #Parsing to the year number
  mutate(relation_length = getYear(relation_length), marriage_length = getYear(marriage_length)) %>%
  mutate(relation_length = (120 - relation_length) %% 100, marriage_length = (120 - marriage_length) %% 100) %>%
  select(-dyadID)
#Note: dyad 7403083 looks incredibly fucky. They don't agree whether they're married, disagree on relationship length by five years, and claim to have 33 children. ????


assembled_dataset <- assembled_dataset %>%
  left_join(last_year_parsed)




### AMBIVALENT SEXISM INDEX CALCULATIONS ###

asi_index <- premeasures %>%
  select(ResponseId, dyadID, starts_with("asi_")) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars) %>%
  mutate_at(vars(asi_7, asi_21), reverseScale6)

corr.test(select(asi_index, starts_with("asi_")))$r

alpha(select(asi_index, starts_with("asi_")))
#Alpha is 0.85 with 7 and 21 reversed. 7 and 13 could probably be dropped, as they're not really correlated with either side, but they're left in for now. 18 is also suspect.

#for now: 
asi_index$asi_score <- rowMeans(select(asi_index, starts_with("asi_")), na.rm = TRUE)
asi_index <- asi_index %>%
  select(ResponseId, dyadID, asi_score)

assembled_dataset <- assembled_dataset %>%
  left_join(asi_index)

rm(asi_index, last_year_parsed)


```

## Participants
```{r include = FALSE}
#demographics<-premeasures %>%
#  full_join(same_sex)%>%
#  full_join(same_race)%>%
#  left_join(assembled_dataset, by = "ResponseId")%>%

# I don't know what was going on here ^^^ but whatever it was was causing the entire document not to knit
# so I rewrote it in a slightly cleaner way
demographics <- premeasures %>%
  select(ResponseId, dyadID, indinc, birthday, Q138, wfh) %>%
  left_join(assembled_dataset) %>%
  select(ResponseId, dyadID,indinc, birthday, couple_race,childnum,Q138,gender,race,wfh)
rm(same_race, same_sex)

```

```{r table1}
dff <- read.table(text = 
"'Annual Income ($)'  73,216    70,726
Age  42.80   6.71
'Number of Children'  1.94     0.89
Gatekeeping  2.91     0.85
'Relationship Satisfaction'  6.57     1.34"
)
names(dff) <- c("Measures","mean","SD")
dff <- printnum(dff)
apa_table(
  dff, 
  caption = "Descriptive Statistics.",
 # note = "This table was created with apa_table()",
  escape = TRUE
)

```

Our sample originally included 182 couples, but exclusion criteria reduced that to 71. 70 of couples were heterosexual, 1 was same-sex female, and no couples were same-sex male. We omitted participants who did not answer questions that were crucial to our analysis. Since our first research question measured the relationship satisfaction of fathers, we omitted the 7 same-sex female couples from our analysis, as well as any couples that did not have children or did not complete the daily diaries. For the analysis of our first hypothesis, there were 70 heterosexual couples. No same-sex male couples in our sample had children. For the second and third hypotheses, as before, we omitted couples without children and who did not complete the daily diaries. Thus, the sample for our first research question included 71 couples, all with at least 1 child. 
 The majority of couples were married (95.8%), while 4.2% were not married but in a committed relationship. Overall, the sample was split evenly between genders, with women making up 51% and men making up 49%. Most of the participants in the sample identified as white (73%), 11% as Asian or Asian American, 8.4% as Black or African American, and 6.3% as Latinx or Hispanic. One individual identified as Middle Eastern, and none replied Other or Prefer not to Answer. 66 couples were same-race and 5 were mixed-race. See Table\ \@ref(tab:table1) for a summary of the sample demographics. The majority of participants reported working from home (65.5%), while 34.5% were either working in person or did not answer. The average age for participants was 42.8 (middle-age) with SD = 6.71. Their average annual income was \$73,216 with a median of \$65,000, and the variance in income was wide with SD = $70,726. All couples had children, with a mean of 1.94 and SD = 0.89. 18 couples from the original sample had discrepancies in the reported number of children, with individuals disagreeing. We used the higher reported number, as we decided that it was more likely for children to be disregarded than fabricated. 
 
```{r include=FALSE, echo=FALSE}
icc_mod  <- gls(relation_qual ~ gender, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID), 
                 data=assembled_dataset)
```


```{r , include=FALSE, echo=FALSE}
coef(icc_mod$model$corStruct, unconstrained = FALSE)
```

## Measures
  **Relationship Satisfaction.** Relationship satisfaction was measured using 25 items from the Relationship Questionnaire [@BraikerH]. Participants answered questions pertaining to their feelings about their partner and the quality of their relationship. Items included, “how much do you feel you ‘give’ to the relationship?” and “how attached do you feel to your partner?” Response options used a 9-part Likert scale ranging from 1 - not at all to 9 - very much. The mean for all 25 items was calculated for the outcome. The scale was reliable with an alpha of .90. The partial intraclass correlation between the two partners’ relationship satisfaction, controlling for gender, was 0.71.  
  **Distribution of Childcare Tasks.** Distribution of childcare tasks was a predictor for fathers' relationship satisfaction and an outcome variable for self-objectification and partner-objectification. For two weeks, participants kept daily diaries in which they recorded if they had spent any time on 16 childcare chores including “helped children with distance learning activities today” and “playing with your child today.” Participants responded by selecting “yes” or “no” for each daily activity. The total number of tasks completed was summed for each participant. The intraclass correlation coefficient between the two partners' childcare task load was 0.63. 
  **Self-Objectification and Partner-Objectification.** Self- and partner-objectification were both measured using 10 of the 12 items from the Self-Objectification Questionnaire [@NollS]. Five of the items pertain to visible characteristics (weight, sex appeal, physical attractiveness, firm/sculpted muscles, and measurements) and five to non-visible characteristics (physical coordination, health, strength, energy level, and physical fitness level). “Coloring” and “coordination” were omitted. For self-objectification, participants ranked how they assigned each characteristic to their own physical self-concept and for partner-objectification they ranked how much they valued each characteristic in their partner. Ranking was done in ascending order from 1 (most) to 10 (least). Scores were found by summing the ranks for visible and non-visible characteristic items separately, and then subtracting the visible characteristics score from the non-visible characteristic score. Scores range from -25 to 25, with higher scores representing a higher level of objectification. The intraclass correlation coefficient for self-objectification was 0.23, and for partner-objectification it was 0.18.   
  **Gatekeeping.** To measure gatekeeping in childcare tasks, eight items pertaining to childcare were used from the Orientation Toward Domestic Labor Questionnaire [@AllenS]. Participants answered to what extent they agreed or disagreed with statements regarding their partner. The questions were worded to be gender-neutral and included, “I like to be in charge when it comes to caring for our child,” and, “My partner doesn’t really know how to do a lot of childcare tasks, so it's just easier if I do them.” Response options used a 5-point Likert scale ranging from 1=strongly disagree to 5=strongly agree. The outcome was calculated using the mean for all eight rows. The scale was reliable with an alpha of .86. The intraclass correlation coefficient for gatekeeping between partners was 0.30. 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results
```{r include = FALSE, echo=FALSE}
assembled_dataset<- read_csv("assembled-dataset.csv")
```

```{r include = FALSE}
fathers<-assembled_dataset%>%
mutate(gatekeep_premeasures = gatekeep_premeasures - mean(assembled_dataset$gatekeep_premeasures, na.rm = TRUE))
```

```{r include = FALSE}
gk_temp_1 <- fathers%>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(gatekeep_P1 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P1)

gk_temp_2 <- fathers%>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(gatekeep_P2 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P2)

fathers<- fathers%>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(gk_temp_1, by = c("dyadID", "ind")) %>%
  left_join(gk_temp_2, by = c("dyadID", "ind")) %>%
  mutate(gatekeep_P = ifelse(is.na(gatekeep_P1), gatekeep_P2, gatekeep_P1)) %>%
  select(-ind, -gatekeep_P2, -gatekeep_P1) %>%
  rename(gatekeep_A = gatekeep_premeasures)

rm(gk_temp_1, gk_temp_2)
```

```{r include = FALSE}
fathers <- fathers 
fathers<-subset(fathers, gender=="Man")
  
#Child_tasks effect for mean gatekeep_A and gatekeep_P (because we grand-mean centered)
mlm1 <- lm(relation_qual ~ childcare_tasks 
            + gatekeep_A + gatekeep_P 
            + childcare_tasks*gatekeep_A + childcare_tasks*gatekeep_P, 
           data = fathers,
           na.action = na.omit)

summary(mlm1)
```
## First Hypothesis  
Our first hypothesis stated that fathers who took on a larger share of childcare tasks would have less relationship satisfaction. Due to the small number of same-sex male dyads in our dataset, we used multiple regression modeling with a non-dyadic dataset, only including men. To arrive at our final regression model, we included childcare tasks, actor's gatekeeping, partner's gatekeeping, the interaction between childcare tasks and actor's gatekeeping, and the interaction between childcare tasks and partner's gatekeeping as predictors.

## Second and Third Hypotheses
Our second and third hypotheses were as follows: that partners who objectified their partner more would take on a smaller role in caring for their children, and that people who objectified themselves more would be more likely to take on an increased load of childcare tasks. We used multilevel modeling and the APIM [@Kenny]. Because our participants were individuals within couples, the APIM allowed us to conduct statistical analyses as multilevel models with indistinguishable dyads to account for the nonindependence and shared variance. 
  Our final model included partner’s partner-objectification and actor’s self-objectification as explanatory variables for the actor's childcare task load. Gender was used as a moderating variable and gatekeeping was used as a control variable. We also modeled the interaction between gender and partner’s partner-objectification. 
During exploratory analysis we tested for actor’s partner-objectification, the moderation of race, ambivalent sexism (both actor and partner) and teleworking status, and several interaction terms. For parsimony, the model was then pared down to only include variables that were significant or nearing significance ($p$ $\leq$ 0.10). Although actor’s partner-objectification was a main explanatory variable for our second hypothesis, it had such a high error term that it was disrupting the coefficient terms for the rest of the model and was thus, dropped, ($b$ = -0.28, $t$ = -0.58, $p$ = 0.561).

## Missing Data
Out of the 364 individuals (182 couples) who answered the questionnaire for the first part of the study, only 265 participated in the later daily diaries portion. Of those, only 147 individuals had children, and only 142 (71 couples) still had partners in the study. Individuals who did not respond to any of the questions used in the model were excluded.

```{r q1table}
df <- read.table(text = 
"'Childcare Tasks'  '< 0.01'   '< 0.01'   0.94
'Gatekeeping Actor'  -0.56    0.32   0.08
'Gatekeeping Partner high'  -0.37    0.30   0.23
'Childcare Tasks x Gatekeeping Actor'  '< 0.01'    '< 0.01'  0.27
'Childcare Tasks x Gatekeeping Partner'  '< 0.01'  '< 0.01'  0.31"
)
names(df) <- c("variable","coefficient"," SE ", "  p-value")
# kbl(df) 
# df%>%
#  kbl( caption = '<b>Relationship Between Predictors and Relationship Satisfaction</b>', format = 'html') %>%
#   kable_styling()


df <- printnum(df)

apa_table(
  df, 
  caption = "Relationship Between Predictors and Relationship Satisfaction.",
 # note = "This table was created with apa_table()",
  escape = TRUE
)
```
## Main Results

## Childcare tasks on father relationship satisfaction
See Table\ \@ref(tab:q1table) for all of the estimates from our final model.
Contrary to our first hypothesis, father childcare task load had no statistically significant effect on relationship satisfaction when actor and partner gatekeeping was at the mean ($b$  $\leq$ 0.01, $SE$ $\leq$ 0.01, $p$ = 0.94).  
When fathers did no childcare tasks, there was no statistically significant effect of either actor's or partner's gatekeeping on relationship satisfaction, ($b$ = -0.56, $SE$ = 0.32, $p$ = 0.08), ($b$ = -0.37, $SE$ = 0.30, $p$ = 0.23). The interaction between performing more childcare tasks and actor's gatekeeping did not have a significant effect on relationship satisfaction for fathers, ($b$  $\leq$ 0.01, $SE$  $\leq$ 0.01, $p$ = 0.27). Similarly, the interaction between performing more childcare tasks and partner's gatekeeping did not have a significant effect on relationship satisfaction for fathers, ($b$  $\leq$ 0.01, $SE$  $\leq$ 0.01, $p$ = 0.31).

## Objectification predicting childcare labor contribution 
See Table\ \@ref(tab:q23table) for the estimates for all coefficients from our final model. Contrary to our second hypothesis, there was no effect of actor’s partner-objectification on childcare task load, ($b$ = -0.28, $t$ = -0.58, $p$ = 0.561). As predicted by our third hypothesis, there was a statistically significant effect of actor’s self-objectification on childcare task load, ($b$ = .85, $t$ = 2.33, $p$ = .021), with individuals who objectified themselves doing more childcare tasks. There was no significant effect of the actor's objectification of their partner on childcare task load, ($b$ = .60, $t$ = 1.39, $p$ = .165). 
Gender had a significant effect on childcare task load, with women on average doing more tasks than men, ($b$ = 14.96, $t$ = 2.37, $p$ = .019). There was a significant interaction between gender and partner’s partner-objectification in a direction contrary to expectations, with women whose partners objectified them more doing fewer tasks than those whose partners objectified them less ($b$ = -1.72, $t$ = -2.57, $p$ = 0.011).

\newpage

```{r include = FALSE}

assembled_dataset <- read_csv("assembled-dataset.csv")

```

```{r include = FALSE}
children_only <- assembled_dataset %>%
  filter(children_any == 1) %>%
  group_by(dyadID) %>%
  summarize(childcare_notNA = sum(childcare_tasks))

children_and_tasks <- assembled_dataset %>%
  left_join(children_only) %>%
  filter(!is.na(childcare_notNA)) %>%
  filter(children_any == 1) %>%
  mutate(gender = ifelse(gender == "Man,Cis gendered", "Man", gender)) %>%
  mutate(gender = ifelse(gender == "Woman,Cis gendered", "Woman", gender)) %>%
  mutate(telework=ifelse(teleworking == c("Yes, I am teleworking but my partner is not", "We are both teleworking"), 0, 1))
rm(children_only)


full_dyads <- children_and_tasks %>%
  group_by(dyadID) %>%
  summarize(n = n())

children_and_tasks <- children_and_tasks %>%
  mutate(gatekeep_premeasures = gatekeep_premeasures - mean(children_and_tasks$gatekeep_premeasures, na.rm = TRUE))

```

```{r include = FALSE}
Basic_Objectification <- gls(childcare_tasks ~ self_obj_score + gender + gender*other_obj_score_P,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

summary(Basic_Objectification)
#Women in general do more tasks than men. People who objectify themselves more do more tasks. Curiously, men whose partners objectify them more do more childcare tasks (though insignificant), and women whose partners objectify them more do fewer childcare tasks. 
```


```{r include = FALSE}
gk_temp_1 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(gatekeep_P1 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P1)

gk_temp_2 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(gatekeep_P2 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P2)

children_and_tasks <- children_and_tasks %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(gk_temp_1, by = c("dyadID", "ind")) %>%
  left_join(gk_temp_2, by = c("dyadID", "ind")) %>%
  mutate(gatekeep_P = ifelse(is.na(gatekeep_P1), gatekeep_P2, gatekeep_P1)) %>%
  select(-ind, -gatekeep_P2, -gatekeep_P1) %>%
  rename(gatekeep_A = gatekeep_premeasures)

rm(gk_temp_1, gk_temp_2)

```

```{r include = FALSE}
cc_temp_1 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(Childcare_P1 = childcare_tasks) %>%
  select(dyadID, ind, Childcare_P1)

cc_temp_2 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(Childcare_P2 = childcare_tasks) %>%
  select(dyadID, ind, Childcare_P2)

children_and_tasks <- children_and_tasks %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(cc_temp_1, by = c("dyadID", "ind")) %>%
  left_join(cc_temp_2, by = c("dyadID", "ind")) %>%
  mutate(childcare_tasks_P = ifelse(is.na(Childcare_P1), Childcare_P2, Childcare_P1)) %>%
  select(-ind, -Childcare_P2, -Childcare_P1) %>%
  rename(childcare_tasks_A = childcare_tasks)

rm(cc_temp_1, cc_temp_2)


```


```{r include = FALSE}
apim_final <- gls(childcare_tasks_A ~ self_obj_score + gender + gender*other_obj_score_P + gatekeep_A,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

coeffs <- coef(apim_final)
summarized <- summary(apim_final)
t_table <- summarized$tTable
t_table <- data.frame(t_table)
row.names(t_table) <- c("Intercept","Self Objectification Score", "Female Gender", "Partner's Partner Objectification", "Gatekeeping", "Partner's Partner Objectification * Female Gender")
t_table <- t_table %>%
  select(-Std.Error) %>%
  rename(B = Value,'t' = t.value, 'p' = p.value)
```

```{r test, include = FALSE}
a <- unname(coeffs)
b <- names(coeffs)
test <- data.frame(a, b)
t_table <- printnum(t_table)
```

```{r q23table}

apa_table(
  t_table, 
  caption = "Effect of Self-Objectification on Childcare Tasks",
  escape = TRUE
)

```

# Discussion
The present study is the first to examine the relationship between objectification and childcare labor in cohabitating romantic partners. Objectification Theory [@FredrickB] has advanced our understanding of the negative mental health outcomes of self-objectification [@BrockR; @MercurioA] and has provided a framework for understanding how self-objectification might negatively impact relationship satisfaction [@DownsD; @ZurbriggenE] and affect women’s participation in gender-based activism [@CalogeroR]. The present study builds on the existing literature of self-objectification by providing evidence that it is a predictor for division of labor within relationships. However, partner-objectification was only a predictor of childcare when controlling for gender. Additionally, our findings regarding fathers’ childcare labor contribution and relationship satisfaction might provide insight that social norms surrounding gender roles and childcare in the United States may be shifting.  
  Based on existing research that indicates that satisfaction is highest in relationships when division of household tasks in a relationship is equal [@CarlsonD], we predicted that fathers who do a larger share of the childcare labor tasks would feel less satisfied in their relationship; our results did not support this hypothesis. Although [@CarlsonDDivision] found that fathers who took on a higher load of childcare than their partner had slightly lower sexual relationship quality, our findings are consistent with [@NewkirkK], who found that childcare labor was not a predictor of conflict for fathers. Neither actor nor partner gatekeeping were significant moderators for the association of childcare and relationship satisfaction. Considering that [@AllenS] found that gatekeepers performed a larger share of childcare, this was surprising. We suspect that the lack of significance may be due to reducing our sample size to include only fathers.  
  Consistent with [@RhoadsS]’s findings, women in our study did more childcare labor overall. However, our hypothesis that individuals who objectified their partners would take on a smaller role in caring for their children was not supported. Additionally, actor partner-objectification did not affect the amount of childcare labor tasks performed by participants' partners, although when moderated for gender, women who were objectified by their partners did fewer childcare tasks. Given our finding that self-objectification did significantly affect childcare tasks and considering the self-perpetuating nature of objectification [@StrelanP; @ZurbriggenE], the lack of significance in our results may be due to the non-independence between self-objectification and partner-objectification, in that partner-objectification directly affected self-objectification rather than affecting childcare tasks.  
 As predicted, individuals who self-objectified performed more childcare labor tasks. Considering objectification theory [@FredrickB], we speculate that this may be because people who self-objectify tend to perform more service tasks because they view themselves as vessels. As expected, we found that women took on a higher share of childcare tasks than men overall, which was consistent with [@RhoadsS]’s findings. This may be due to societal expectations of mothers as the primary caretaker of children [@BroseS; @RadcliffeL]. A possible explanation for why our hypothesis for self-objectification was supported while our hypothesis for partner objectification was not could be because individuals who objectify their partners, might idealize rather than dehumanize them and, as a result, help them more with time-consuming, menial tasks like childcare.
 
## Limitations and Future Directions
The current study is limited in several ways. First, because our sample did not include any same-sex male couples, we were unable to test our first hypothesis with same-sex dyads. Since childcare is affected by societal norms that place mothers as the primary caretaker of children [@BroseS; @RadcliffeL], future work should use multi-level modeling to examine childcare and relationship satisfaction in LGBTQI+ couples. Second, we did not collect data on the gender of participants’ children, so we were not able to explore the interaction effect of child and parent gender on childcare labor. Future research can measure this interaction to assess stereotypes around gender-based parental favoritism.  Third, we suspect, that childcare reports had many missing values due to parents sometimes forgetting to update their daily tasks diaries, which might have affected the accuracy of our results. Future studies could use interviews or task-tracking technologies to measure the number of childcare tasks that parents performed. Fourth, because most of our couples were white, same-race, heterosexual, and teleworking, our findings cannot be generalized to the entire population. Additionally, because our study was conducted during the COVID-19 pandemic when fathers were working from home, and likely spent more time caring for their children [@CarlsonD; @ChungH], our results might may not capture the general childcare dynamics of couples during pre- and post-pandemic times.  
  Finally, in light of our surprising results that individuals who objectified their partners did not do less childcare labor, future research warrants investigation into different aspects of objectification. While much of the existing research has shown how objectification dehumanizes, it is possible that partner-objectification might also include idealizing one's partner. 
  
## Conclusion 
The current study extended objectification theory by giving insight into how childcare labor is divided when self-objectification is present in a relationship. Individuals who self-objectified performed more childcare labor tasks than their partners, regardless of gender. This study is the first to examine the dynamics of childcare labor in the context of objectification in a dyadic framework of cohabiting couples. Results could inform practitioners seeking to help couples reduce conflict through taking self-objectification into account as a possible contributor of marital strife due to an unequal division of household labor. Although individuals who partner-objectified did not perform a lesser share of childcare labor as predicted, this result may indicate that objectification theory's focus on the dehumanizing aspects of objectification might be too narrow. Additionally, we did not find evidence to support our expectations that fathers who performed a larger share of childcare tasks would experience less relationship satisfaction, which might be indicative of changing attitudes regarding traditional gender roles and childcare in the United States. Despite study limitations, our findings provide important insight for the future direction of research on gender roles and objectification theory.


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
