---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "annotated.bib"]
nocite            : |
  @CarlsonDDivision, @RhoadsS, @StrelanP, @ZurbriggenE, @RamseyL, @NewkirkK, @ChungH, @BleskeRechekA, @RhoadsS, @RadcliffeL, @ChickK, @BroseS, @SullivanO, @CraigL, @IshiiM, @WangR, @CarlsonD, @ChungH, @BjarnasonT, @DownsD, @RamseyL, @MaharE, @BrockR, @MercurioA, @CalogeroR, @FredrickB

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Equitable division of childcare labor increases relationship satisfaction in cohabiting couples [@CarlsonDDivision]. Conversely, partner-objectification decreases relationship satisfaction for both men and women [@StrelanP; @ZurbriggenE] via self-objectification [@RamseyL]. The aim of the current study was to examine the division of childcare labor in a dyatic framework of cohabiting couples.  
  Mothers continue to take on a larger share of childcare labor, even in dual-earning households [@RhoadsS]. Factors that may prevent fathers from becoming more involved with childcare include traditional gender-oriented attitudes regarding childcare labor [@RadcliffeL; @BroseS] and maternal gatekeeping [@AllenS]. We sought to understand if men who act counter to societal gender norms by performing a majority of the childcare tasks would experience reduced relationship satisfaction. To our knowledge, this is the first study to examine associations between objectification and childcare labor roles. The current study looks to broaden the academic literature on objectification by examining if partner-objectification and self-objectification influence the distribution of childcare labor tasks.
  
**Childcare labor and gender roles**  
Cohabitating couples report less relationship conflict and higher relationship quality when the division of childcare labor is equitable [@NewkirkK; @CarlsonDDivision]. Despite this, women generally take on a larger share of childcare tasks than men [@ChungH; @BleskeRechekA], even when both partners have similar work obligations. In a study that examined married couples in which both partners were tenure track professors, fathers performed fewer childcare tasks than mothers, even when fathers held an egalitarian attitude toward childcare labor [@RhoadsS].  
  Although women reported enjoying childcare tasks more than men [@BleskeRechekA], this may be due more to societal expectations that position women as the primary caretaker of children [@RadcliffeL] rather than a biological drive. Socialization of gender roles begins in infancy, with boys and girls receiving different gendered messaging from caretakers. Boys receive more attention from daycare workers and are more likely to receive comments about their size and physical abilities while girls are more likely to be reinforced for their appearance and helping behaviors [@ChickK]. These types of messages teach young children that a girl’s role is oriented toward domestic work [@ChickK] while boys are better suited for labor. In one study, most adolescents chose the mother as the parent who should stay home to care for children in equal earning couples, citing women’s social role as caretakers as a primary reason [@BroseS].  
  However, gender normative views on childcare might not be static. Very low fertility countries that have recently seen an increase in fertility rates also saw an increase in childcare labor contributions from young, more highly educated fathers [@SullivanO]. These countries also saw a corresponding decline in the percentage of men agreeing with the statement, “A man’s job is to earn money; a woman’s job is to look after the home and family” [@SullivanO], suggesting social diffusion of a change in attitudes toward gender roles and domestic labor. Additionally, men with higher levels of education [@CraigL; @SullivanO], lower levels of work-related stress [@IshiiM], and more family-oriented work environments [@IshiiM] are more likely to be involved in childcare labor.   
  As mothers’ participation in the workforce has increased, so has fathers’ involvement in childcare labor [@WangR]. Recently, fathers who have transitioned to work-from-home positions due to restrictions from the Covid-19 pandemic have increased the amount of time spent taking care of children [@CarlsonD; @ChungH]. While couples reported better relationship quality when fathers were more involved in childcare [@CarlsonD], and men reported higher relationship satisfaction when the division of household tasks was equitable [@BjarnasonT], men who spent more time on childcare tasks than their partner experienced reduced sexual satisfaction in their relationships [@CarlsonD]. We predicted that men who subvert traditional gender roles by performing a larger share of childcare labor than their partners would experience lower relationship satisfaction. 

**Objectification and Relationships**  
Objectification involves treating a person as an object rather than a being with thoughts and feelings [@FredrickB]. Higher levels of objectification in the context of a romantic relationship may harm relationship quality for both the person being objectified and the objectifier [@DownsD; @ZurbriggenE; @StrelanP; @RamseyL; @MaharE]. People who were objectified by their partner reported less satisfaction in their relationships [@DownsD; @ZurbriggenE]. Additionally, people who objectified their partner reported reduced relationship satisfaction [@ZurbriggenE], although one study found support for this only with women who objectified their partner [@MaharE]. Some aspects of objectification appear to affect men more than women. Men were more likely to objectify their partner than women. Additionally, men who engaged in objectification reported less relationship commitment and were more likely to believe they had higher-quality relationship alternatives [@MaharE]. Lower sexual satisfaction was also associated with both partner- and self-objectification in men [@ZurbriggenE]. However, there were no differences in self-objectification between men and women [@ZurbriggenE], and lower partner objectification was associated with increased sexual satisfaction in both men and women [@BrockR].  
  There is evidence that objectification has implications on personal well-being. Self-objectification has been associated with lower life satisfaction [@MercurioA], although research is mixed. Predicted associations between self-objectification and reduced self-esteem have been supported [@MercurioA; @StrelanP]; however, there is no consensus about the link between self-objectification and body esteem. While one study found no association between self-objectification and reduced body esteem [@StrelanP], a later study supported a path between self-objectification and reduced self-esteem through body esteem [@MercurioA]. Neither body-esteem nor self-esteem was associated with partner-objectification [@StrelanP]. The absence of objectification predicted slightly more positive outcomes; in a study examining pregnant women and objectification, both men and women who felt humanized by their partner reported fewer depression symptoms [@BrockR].   
 	Partner- and self-objectification seem to be linked and self-perpetuating. People who other- and self-objectify are more likely to be in relationships with partners who also other- and self-objectify. Additionally, the more that someone is objectified, the more likely they are to self-objectify, which makes them more likely to objectify others [@StrelanP; @ZurbriggenE]. One study found that heterosexual women who enjoy being sexualized are more likely to feel objectified by their partner, leading to lower relationship satisfaction via increased self-objectification [@RamseyL]. Another study found that exotic dancers, sexualized by trade, reported feeling objectified more and having lower relationship satisfaction than college women; however, when moderated for sexual preference, college women and heterosexual exotic dancers had similar levels of relationship satisfaction, with bisexual dancers reporting lower satisfaction with their relationships [@DownsD].  
  A possible consequence of objectification has societal implications beyond the scope of relationships and personal wellness. One study found evidence that women who self-objectify are more likely to support and justify gender norms that support sexist ideologies. These women were less likely to engage in social activism centered on gender inequalities [@CalogeroR]. However, a subsequent study failed to replicate these findings [@DewildeM]. The current research sought to expand on this literature by examining the association between objectification and childcare labor. We predicted that partner-objectification would predict a lower contribution to childcare labor, while self-objectification would predict a higher contribution for both men and women.  
  
**Current study**  
The current study examined the role of childcare labor in relationship satisfaction for men in both heterosexual and same-sex cohabiting relationships. Because it is often a barrier to performing childcare tasks, we controlled for gatekeeping, which consists of beliefs and behaviors that limit equal partner participation [@AllenS]. Due to societal norms in the US that place mothers as the primary caretaker of children [@RadcliffeL; @BroseS], our first hypothesis was that fathers who take on a larger share of the childcare labor tasks would have decreased relationship satisfaction.  
  The current study is the first to examine objectification in the context of childcare. We used Actor Partner Independence Modeling to test our second and third research questions, moderating for gender and mediating for ambivalent sexism. One characteristic of objectification is viewing a person as a vessel; thus, our second hypothesis was that people who objectify their partner would perform less childcare labor than their partner. Finally, building on previous research positively correlating partner-objectification with self-objectification [@StrelanP; @ZurbriggenE], our third hypothesis was that partners who self-objectify would perform a larger share of the childcare labor.







\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
