---
title             : "measures"
shorttitle        : "Title"

author: 
  - name          : "Angela Jauregui"
    affiliation   : "1"
  - name          : "Lauren Meyer"
    affiliation   : "1"
  - name          : "Syrine Matoussi"
    affiliation   : "1"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Smith College"


  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Measures:

#  Preliminary Analyses:
Include a section called Demographics or Participants or
Participant Demographics or Preliminary Analyses. This is either a subsection of the
Method section, or the Results section, depending on how involved it gets. You can be
creative in this section, but here are some suggested things to include:
o Describe any exclusion criteria used: for the first question we are exluding lesbain couples.
those would din't answer all of the questions NA values for important questions for analysis 

o Report sample size (number of individuals as well as number of dyads).
o Demographics for the sample. That is, percentages of gender,
percentages of racial groups, participant age, major, income, age of children,
adoption type:

o If working with indistinguishable dyads same-gender and different-gender couples:

o If working with distinguishable dyads, report the correlations among important
study variables using the dyad dataset. I recommend doing this in a table, NOT by
reporting each correlation in the text:

o If working with distinguishable dyads, you can run some paired-samples t-tests
using the dyad dataset to test for basic differences:

o If working with all the same-gender couples in Goldberg, you can do some
independent samples t-tests to examine differences in between-dyads variables
(e.g., is relationship length different between Lesbian and Gay male couples?). To
do this, using the individual or pairwise data, you will need to first filter for
member 1 so there’s only one record per couple. Then you can do your t-test.

# table/figure: 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
