---
title             : "Measures and Descriptive Statistics"
shorttitle        : "Measures"

author: 
  - name          : "Angela Jauregui"
    # affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
  - name          : "Lauren Meyer"
    #affiliation   : "1"  
  - name          : "Syrine Matoussi"
    # affiliation   : "1"
    role:


affiliation:
  - id            : " "
    institution   : "Smith College"



abstract: | 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "paper-references.bib", "annotated.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(mosaic)
library(lubridate)
library(nlme)
r_refs("r-references.bib")
```


```{r analysis-preferences, include = FALSE}

# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r include = FALSE, echo=FALSE}
#library(tidyverse)
library(dplyr)
library(readr)
library(psych)
library(kableExtra)

dailydiary <- read_csv("TeleCom_Dyad_dailydiary.csv")
premeasures <- read_csv("TeleCom_Dyad_premeasures.csv")
#view(premeasures)

#Simple helper function to convert "Yes" and "No" to 1 and 0 for summing
YesNo <- function(x){
    ifelse(x=="Yes", 1,0)
}

stripChars <- function(x) {
  parse_number(x)
}

reverseScale9 <- function(x) {
  1 + 9 - x
}

reverseScale6 <- function(x) {
  7 - x
}


### Basic Data Cleaning, Chores Calculations

filter_children <- premeasures %>%
  select(ResponseId, dyadID, people_4_TEXT, people_5_TEXT) %>%
  mutate(people_4_TEXT = ifelse(is.na(people_4_TEXT), 0, people_4_TEXT)) %>%
  mutate(people_5_TEXT = ifelse(is.na(people_5_TEXT), 0, people_5_TEXT)) %>%
  mutate(children = ifelse(people_4_TEXT > 0, 1, ifelse(people_5_TEXT > 0, 1, 0)), childnum = people_4_TEXT + people_5_TEXT, na.rm = TRUE) %>%
  select(ResponseId, children, childnum)

clean_dd <- dailydiary %>%
  select(partID, dyadID, gender, homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding) %>%
  mutate_at(vars(-partID, -dyadID, -gender),YesNo) %>%
  mutate_if(is.numeric, funs(ifelse(is.na(.), 0, .)))

chores_final <- inner_join(clean_dd, filter_children, by = c("partID" = "ResponseId")) %>%
  filter(children == 1) %>%
  mutate(total_chores = rowSums(across(c(homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding), na.rm = TRUE))) %>%
  group_by(partID) %>%
  summarize(total_chores = sum(total_chores))

rm(clean_dd)


### Self and Other Objectification Calculations

comp_v <- c(1,2,4,7,9)
attr_v <- c(3,5,6,8,10)
self_obj <- premeasures %>%
  select(ResponseId, dyadID, `self-object_1`, `self-object_2`, `self-object_3`, `self-object_4`, `self-object_5`, `self-object_6`, `self-object_7`, `self-object_8`, `self-object_9`, `self-object_10`) %>%
  mutate(comp = `self-object_1` + `self-object_2` + `self-object_4` + `self-object_7` + `self-object_9`, attr = `self-object_3` + `self-object_5` + `self-object_6` + `self-object_8` + `self-object_10`) %>%
  mutate(self_obj_score = comp - attr) %>%
  mutate(self_obj_score = ifelse(is.na(`self-object_1`), NA, self_obj_score)) 
#Confirming that they correlate at -1
corr.test(select(self_obj, comp, attr))
self_obj <- self_obj %>%
  select(ResponseId, dyadID, self_obj_score)
rm(comp_v, attr_v)

other_obj <- premeasures %>%
  select(ResponseId, dyadID, `other-object_1`, `other-object_2`, `other-object_3`, `other-object_4`, `other-object_5`, `other-object_6`, `other-object_7`, `other-object_8`, `other-object_9`, `other-object_10`) %>%
  mutate(comp = `other-object_1` + `other-object_2` + `other-object_4` + `other-object_7` + `other-object_9`, attr = `other-object_3` + `other-object_5` + `other-object_6` + `other-object_8` + `other-object_10`) %>%
  mutate(other_obj_score = comp - attr) %>%
  mutate(other_obj_score = ifelse(is.na(`other-object_1`), NA, other_obj_score)) 
corr.test(select(other_obj, comp, attr))
other_obj <- other_obj %>%
  select(ResponseId, other_obj_score)

objectification <- inner_join(self_obj, other_obj, by = c("ResponseId" = "ResponseId")) 
temp_obj_1 <- objectification %>%
  #adding an alternating index for use in APIM calculations
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(self_obj_score_P1 = self_obj_score, other_obj_score_P1 = other_obj_score) %>%
  select(dyadID, ind, self_obj_score_P1, other_obj_score_P1)

temp_obj_2 <- objectification %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(self_obj_score_P2 = self_obj_score, other_obj_score_P2 = other_obj_score) %>%
  select(-ResponseId)

objectification <- objectification %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(temp_obj_1, by = c("dyadID", "ind")) %>%
  left_join(temp_obj_2, by = c("dyadID", "ind")) %>%
  mutate(self_obj_score_P = ifelse(is.na(self_obj_score_P1), self_obj_score_P2, self_obj_score_P1)) %>%
  mutate(other_obj_score_P = ifelse(is.na(other_obj_score_P1), other_obj_score_P2, other_obj_score_P1)) %>%
  select(ResponseId, dyadID, self_obj_score, other_obj_score, self_obj_score_P, other_obj_score_P)



rm(self_obj, other_obj, temp_obj_1, temp_obj_2)

### Relationship Satisfaction Calculations and Alpha

rel_qual <- premeasures %>%
  select(ResponseId, dyadID, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars) %>%
  #These are the ones being reversed
  mutate_at(vars(relation_qual_2, relation_qual_4, relation_qual_7, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_18, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24), reverseScale9)

corr.test(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))$r
#23 might be worth dropping, but the alpha is high enough (0.9) that we don't *need* to drop anything
alpha(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))

#Final calculation
rel_qual$total_relation_qual <- rowMeans(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25), na.rm = TRUE)
rel_qual <- rel_qual %>%
  select(ResponseId, dyadID, total_relation_qual)


### Gatekeeping Calculations and Alpha

gatekeep <- premeasures %>%
  select(ResponseId, dyadID, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars)

corr.test(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#looking good, nothing needs to be reversed

alpha(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#.92 alpha, nothing that looks like it needs reversing

gatekeep$gatekeep_total <- rowMeans(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15), na.rm = TRUE)

gatekeep <- gatekeep %>% 
  select(ResponseId, dyadID, gatekeep_total)

scaleToNumeric <- function(x) {
  ifelse(x == "Strongly agree", 5, ifelse(x == "Somewhat agree", 4, ifelse(x == "Neither agree nor disagree", 3, ifelse(x == "Somewhat disagree", 2, ifelse(x == "Strongly disagree", 1, NA)))))
}

dd_gatekeep <- dailydiary %>%
  select(partID, dyadID, gate1, gate2, gate3, gate4, gate5, gate6) %>%
  mutate_at(vars(gate1, gate2, gate3, gate4, gate5, gate6), scaleToNumeric)

corr.test(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#no negative correlations again! we good.

alpha(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#alpha of 0.84. Just fine. 1 and 4 could get dropped but it's consistent enough as is. 

dd_gatekeep$gateTotal <- rowMeans(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6), na.rm = TRUE)
dd_gatekeep <- dd_gatekeep %>%
  group_by(partID) %>%
  summarize(dd_gateTotal = mean(gateTotal))

### Assembling the tables together

assembled_dataset <- premeasures %>%
  select(ResponseId, dyadID, gender, race, Q139) %>%
  inner_join(., objectification) %>%
  inner_join(., rel_qual) %>%
  rename(relation_qual = total_relation_qual) %>%
  left_join(., gatekeep) %>%
  rename(gatekeep_premeasures = gatekeep_total) %>%
  left_join(dd_gatekeep, by = c("ResponseId" = "partID")) %>%
  rename(gatekeep_diaries = dd_gateTotal) %>%
  left_join(chores_final, by = c("ResponseId" = "partID")) %>%
  rename(childcare_tasks = total_chores) %>%
  left_join(filter_children) %>%
  rename(children_any = children) %>%
  rename(teleworking = Q139)

#cleanup
rm(objectification, rel_qual, gatekeep, dd_gatekeep, chores_final, filter_children)

total_childcare_temp <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  group_by(dyadID) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  summarize(total_tasks = sum(childcare_tasks)) %>%
  filter(total_tasks > 0)

childcare_temp2 <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  left_join(total_childcare_temp) %>%
  filter(total_tasks > 0) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  mutate(childcare_percent = childcare_tasks / total_tasks * 100) %>%
  select(ResponseId, childcare_percent)

assembled_dataset <- assembled_dataset %>%
  left_join(childcare_temp2)

#cleanup
rm(total_childcare_temp, childcare_temp2)

### Calculating the existence and number of children, and the number of discrepencies

#Initial Corrections: 
#The number of children entered by R_3Jgt1VbMKwbyTKE seems to be a typo, entered 10, partner put 0. 
assembled_dataset <- assembled_dataset %>%
  mutate(childnum = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, childnum), children_any = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, children_any))


children <- assembled_dataset %>%
  select(ResponseId, dyadID, children_any, childnum) %>%
  group_by(dyadID)

maxchildren <- children %>%
  summarize(children_max = max(childnum))

children_discrep <- children %>%
  left_join(maxchildren) %>%
  mutate(child_diff = children_max - childnum) %>%
  filter(child_diff > 0)
#there were 18 respondents who reported fewer children than their partners. 

rm(maxchildren, children)

### Same Sex Relationship and Same Race Relationship markers

same_sex <- assembled_dataset %>%
  mutate(gender = ifelse(gender == "Man", 0, 1)) %>%
  group_by(dyadID) %>%
  summarize(couple = sum(gender)) %>%
  mutate(couple = ifelse(couple == 0, "Same-sex Male", ifelse(couple == 1, "Different-sex", "Same-sex Female")))
assembled_dataset <- assembled_dataset %>%
  left_join(same_sex, by = "dyadID") %>%
  rename(couple_genders = couple)


same_race <- assembled_dataset %>%
  group_by(dyadID, race) %>%
  summarize(n = n()) %>%
  mutate(couple_race = ifelse(n == 2, "Same Race", "Mixed Race")) %>%
  select(dyadID, couple_race) %>%
  distinct()
assembled_dataset <- assembled_dataset %>%
  left_join(same_race, by = c("dyadID" = "dyadID"))


### Marriage and Relationship Lengths, in years. Did not resolve disagreements. 

getYear <- function(x){
  parse_number(substr(x, nchar(x)-1, nchar(x)))
}
last_year_parsed <- premeasures %>%
  select(ResponseId, dyadID, relation_length, married, marriage_length) %>%
  #Parsing to the year number
  mutate(relation_length = getYear(relation_length), marriage_length = getYear(marriage_length)) %>%
  mutate(relation_length = (120 - relation_length) %% 100, marriage_length = (120 - marriage_length) %% 100) %>%
  select(-dyadID)
#Note: dyad 7403083 looks incredibly fucky. They don't agree whether they're married, disagree on relationship length by five years, and claim to have 33 children. ????


assembled_dataset <- assembled_dataset %>%
  left_join(last_year_parsed)




### AMBIVALENT SEXISM INDEX CALCULATIONS ###

asi_index <- premeasures %>%
  select(ResponseId, dyadID, starts_with("asi_")) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars) %>%
  mutate_at(vars(asi_7, asi_21), reverseScale6)

corr.test(select(asi_index, starts_with("asi_")))$r

alpha(select(asi_index, starts_with("asi_")))
#Alpha is 0.85 with 7 and 21 reversed. 7 and 13 could probably be dropped, as they're not really correlated with either side, but they're left in for now. 18 is also suspect.

#for now: 
asi_index$asi_score <- rowMeans(select(asi_index, starts_with("asi_")), na.rm = TRUE)
asi_index <- asi_index %>%
  select(ResponseId, dyadID, asi_score)

assembled_dataset <- assembled_dataset %>%
  left_join(asi_index)

rm(asi_index, last_year_parsed)


```


##  Participants:

```{r include = FALSE}
#demographics<-premeasures %>%
#  full_join(same_sex)%>%
#  full_join(same_race)%>%
#  left_join(assembled_dataset, by = "ResponseId")%>%

# I don't know what was going on here ^^^ but whatever it was was causing the entire document not to knit
# so I rewrote it in a slightly cleaner way
demographics <- premeasures %>%
  select(ResponseId, dyadID, indinc, birthday, Q138, wfh) %>%
  left_join(assembled_dataset) %>%
  select(ResponseId, dyadID,indinc, birthday, couple_race,childnum,Q138,gender,race,wfh)
rm(same_race, same_sex)

```

```{r table1}
dff <- read.table(text = 
"'Annual Income ($)'  76,618.80    105,704.12
Age  45.80   8.35
'Number of Children'  1.34     2.17
Gatekeeping  3.00     0.92
'Relationship Satisfaction'  6.47     1.31"
)
names(dff) <- c("Measures","mean","SD")
dff <- printnum(dff)
apa_table(
  dff, 
  caption = "Descriptive Statistics.",
 # note = "This table was created with apa_table()",
  escape = TRUE
)

```


The current study included 182 couples. 172 couples were heterosexual, 7 were same-sex female, and 3 were same-sex male. The majority of couples were married (91.8%), while 8.2% were not married but in a committed relationship. Overall, the sample was split evenly between genders, with women making up 51% and men making up 49%. Most of the participants in the sample identified as white (74%), 10% as Asian or Asian American, 6.6% as Black or African American, and 5.8% as Latinx or Hispanic. 4 individuals identified as Middle Eastern, and 5 replied Other or Prefer not to Answer. See Table\ \@ref(tab:table1) for a summary of the sample demographics. The majority of the individuals reported working from home (61.5%), 20% were working in person, and 18.5% did not answer the question or reported Other. The average age for participants was 45.8 (middle-age) with SD = 8.35. Their average annual income was \$76,618 with a median of \$60,000, and the variance in income was wide with a SD = $105,704. 120 couples had children, while 62 did not. Finally, the reported number of children had a mean of 1.34 but the variance was large across the couples with an SD = 2.17. 18 couples had discrepancies in the reported number of children, with individuals disagreeing. We used the higher reported number, as we decided that it was more likely for children to be disregarded than fabricated. 

  We omitted participants who did not answer questions that were crucial to our analysis. Since our first research question measured the relationship satisfaction among fathers, we omitted the 7 same-sex female couples from that part of the analysis. For the analysis of the first hypothesis there were 172 different-gender couples and 3 same-sex male couples. For the second and third hypotheses, couples needed to have children and have completed the daily diaries portion of the study, so that sample had 71 couples, 69 different-sex and 2 same-sex female, all with at least one child. 161 couples were same-race and 21 were mixed-race.

```{r include=FALSE, echo=FALSE}
icc_mod  <- gls(relation_qual ~ gender, 
                 na.action=na.omit, 
                 correlation=corCompSymm (form=~1|dyadID), 
                 data=assembled_dataset)
```


```{r , include=FALSE, echo=FALSE}
coef(icc_mod$model$corStruct, unconstrained = FALSE)
```

## Measures:

  **Relationship Satisfaction.** Relationship satisfaction was measured using 25 items from the Relationship Questionnaire [@BraikerH]. Participants answered questions pertaining to their feelings about their partner and the quality of their relationship. Items included, “how much do you feel you ‘give’ to the relationship?” and “how attached do you feel to your partner?” Response options used a 9-part Likert scale ranging from 1 - not at all to 9 - very much. The mean for all 25 items was calculated for the outcome.The scale was reliable with an alpha of .90. The partial intraclass correlation between the two partners’ relationship satisfaction, controlling for gender, was 0.71.
  
  **Distribution of Childcare Tasks.** Distribution of childcare tasks was a predictor for fathers' relationship satisfaction, and an outcome variable for self-objectification and partner-objectification. For two weeks, participants kept daily diaries in which they recorded if they had spent any time on 16 childcare chores including “helped children with distance learning activities today” and “playing with your child today.” Participants responded by selecting “yes” or “no” for each daily activity. A total number of tasks completed was summed for each participant. The intraclass correlation coefficient between the two partners' childcare task load was 0.63. 
  	
  **Self-Objectification and Partner-Objectification.** Self- and partner-objectification were both measured using 10 of the 12 items from the Self-Objectification Questionnaire [@NollS]. Five of the items pertain to visible characteristics (weight, sex appeal, physical attractiveness, firm/sculpted muscles, and measurements) and five to non-visible characteristics (physical coordination, health, strength, energy level, and physical fitness level). “Coloring” and “coordination” were omitted. For self-objectification, participants ranked how they assigned each characteristic to their own physical self-concept and for partner-objectification they ranked how much they valued each characteristic in their partner. Ranking was done in ascending order from 1 (most) to 10 (least). Scores were found by summing the ranks for visible and non-visible characteristic items separately, and then subtracting the visible characteristics score from the non-visible characteristic score. Scores range from -25 to 25, with higher scores representing a higher level of objectification. The intraclass corellation coefficient for self-objectification was 0.23, and for partner-objectification it was 0.18. 
  	
  	
  **Gatekeeping.** To measure gatekeeping in childcare tasks, eight items pertaining to childcare were used from the Orientation Toward Domestic Labor Questionnaire [@AllenS]. Participants answered to what extent they agreed or disagreed with statements regarding their partner. The questions were worded to be gender neutral and included “I like to be in charge when it comes to caring for our child” and “My partner doesn’t really know how to do a lot of childcare tasks, so it's just easier if I do them.” Response options used a 5-point Likert scale ranging from 1=strongly disagree to 5=strongly agree. The outcome was calculated using the mean for all eight rows. The scale was reliable with an alpha of .86. The intraclass corellation coefficient for gatekeeping between partners was 0.30. 




## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.



```{r  include=FALSE}
children_only <- assembled_dataset %>%
  filter(children_any == 1) %>%
  group_by(dyadID) %>%
  summarize(childcare_notNA = sum(childcare_tasks))

children_and_tasks <- assembled_dataset %>%
  left_join(children_only) %>%
  filter(!is.na(childcare_notNA)) %>%
  filter(children_any == 1)
rm(children_only)


library(nlme)
mlm <- gls(childcare_tasks ~ self_obj_score + other_obj_score + self_obj_score * other_obj_score,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

summary(mlm)


apim_in <- gls(childcare_tasks ~ self_obj_score_P + other_obj_score,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

summary(apim_in)

#looks interesting so far!
```




\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup