---
title             : "Project Proposal"
shorttitle        : "Proposal"

author: 
  - name          : "Angela Jauregui"
    # affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
  - name          : "Lauren Meyer"
    #affiliation   : "1"  
  - name          : "Syrine Matoussi"
    # affiliation   : "1"
    role:


affiliation:
  - id            : " "
    institution   : "Smith College"



abstract: | 
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "paper-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

```{r setup, include = FALSE}
library("papaja")
library(mosaic)
library(lubridate)
r_refs("r-references.bib")
```


```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r include = FALSE, echo=FALSE}
library(tidyverse)
library(readr)
library(psych)

dailydiary <- read_csv("TeleCom_Dyad_dailydiary.csv")
premeasures <- read_csv("TeleCom_Dyad_premeasures.csv")
#view(premeasures)

#Simple helper function to convert "Yes" and "No" to 1 and 0 for summing
YesNo <- function(x){
    ifelse(x=="Yes", 1,0)
}

stripChars <- function(x) {
  parse_number(x)
}

reverseScale9 <- function(x) {
  1 + 9 - x
}

filter_children <- premeasures %>%
  select(ResponseId, dyadID, people_4_TEXT, people_5_TEXT) %>%
  mutate(people_4_TEXT = ifelse(is.na(people_4_TEXT), 0, people_4_TEXT)) %>%
  mutate(people_5_TEXT = ifelse(is.na(people_5_TEXT), 0, people_5_TEXT)) %>%
  mutate(children = ifelse(people_4_TEXT > 0, 1, ifelse(people_5_TEXT > 0, 1, 0)), childnum = people_4_TEXT + people_5_TEXT, na.rm = TRUE) %>%
  select(ResponseId, children, childnum)

clean_dd <- dailydiary %>%
  select(partID, dyadID, gender, homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding) %>%
  mutate_at(vars(-partID, -dyadID, -gender),YesNo) %>%
  mutate_if(is.numeric, funs(ifelse(is.na(.), 0, .)))

chores_final <- inner_join(clean_dd, filter_children, by = c("partID" = "ResponseId")) %>%
  filter(children == 1) %>%
  mutate(total_chores = rowSums(across(c(homeschool, attention, worrying, activities, clothes, sick, getting_up, put_to_bed, discipline, reading, playing, picking_up, hygiene, dressing, comforting, feeding), na.rm = TRUE))) %>%
  group_by(partID) %>%
  summarize(total_chores = sum(total_chores))

rm(clean_dd)

comp_v <- c(1,2,4,7,9)
attr_v <- c(3,5,6,8,10)
self_obj <- premeasures %>%
  select(ResponseId, dyadID, `self-object_1`, `self-object_2`, `self-object_3`, `self-object_4`, `self-object_5`, `self-object_6`, `self-object_7`, `self-object_8`, `self-object_9`, `self-object_10`) %>%
  mutate(comp = `self-object_1` + `self-object_2` + `self-object_4` + `self-object_7` + `self-object_9`, attr = `self-object_3` + `self-object_5` + `self-object_6` + `self-object_8` + `self-object_10`) %>%
  mutate(self_obj_score = comp - attr) %>%
  mutate(self_obj_score = ifelse(is.na(`self-object_1`), NA, self_obj_score)) 
#Confirming that they correlate at -1
corr.test(select(self_obj, comp, attr))
self_obj <- self_obj %>%
  select(ResponseId, dyadID, self_obj_score)
rm(comp_v, attr_v)

other_obj <- premeasures %>%
  select(ResponseId, dyadID, `other-object_1`, `other-object_2`, `other-object_3`, `other-object_4`, `other-object_5`, `other-object_6`, `other-object_7`, `other-object_8`, `other-object_9`, `other-object_10`) %>%
  mutate(comp = `other-object_1` + `other-object_2` + `other-object_4` + `other-object_7` + `other-object_9`, attr = `other-object_3` + `other-object_5` + `other-object_6` + `other-object_8` + `other-object_10`) %>%
  mutate(other_obj_score = comp - attr) %>%
  mutate(other_obj_score = ifelse(is.na(`other-object_1`), NA, other_obj_score)) 
corr.test(select(other_obj, comp, attr))
other_obj <- other_obj %>%
  select(ResponseId, other_obj_score)

objectification <- inner_join(self_obj, other_obj, by = c("ResponseId" = "ResponseId")) 
temp_obj_1 <- objectification %>%
  #adding an alternating index for use in APIM calculations
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(self_obj_score_P1 = self_obj_score, other_obj_score_P1 = other_obj_score) %>%
  select(dyadID, ind, self_obj_score_P1, other_obj_score_P1)

temp_obj_2 <- objectification %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(self_obj_score_P2 = self_obj_score, other_obj_score_P2 = other_obj_score) %>%
  select(-ResponseId)

objectification <- objectification %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(temp_obj_1, by = c("dyadID", "ind")) %>%
  left_join(temp_obj_2, by = c("dyadID", "ind")) %>%
  mutate(self_obj_score_P = ifelse(is.na(self_obj_score_P1), self_obj_score_P2, self_obj_score_P1)) %>%
  mutate(other_obj_score_P = ifelse(is.na(other_obj_score_P1), other_obj_score_P2, other_obj_score_P1)) %>%
  select(ResponseId, dyadID, self_obj_score, other_obj_score, self_obj_score_P, other_obj_score_P)



rm(self_obj, other_obj, temp_obj_1, temp_obj_2)

rel_qual <- premeasures %>%
  select(ResponseId, dyadID, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars) %>%
  #These are the ones being reversed
  mutate_at(vars(relation_qual_2, relation_qual_4, relation_qual_7, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_18, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24), reverseScale9)

corr.test(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))$r
#23 might be worth dropping, but the alpha is high enough (0.9) that we don't *need* to drop anything
alpha(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25))

#Final calculation
rel_qual$total_relation_qual <- rowMeans(select(rel_qual, relation_qual_1, relation_qual_2, relation_qual_3, relation_qual_4, relation_qual_5, relation_qual_6, relation_qual_7, relation_qual_8, relation_qual_9, relation_qual_10, relation_qual_11, relation_qual_12, relation_qual_13, relation_qual_14, relation_qual_15, relation_qual_16, relation_qual_17, relation_qual_18, relation_qual_19, relation_qual_20, relation_qual_21, relation_qual_22, relation_qual_23, relation_qual_24, relation_qual_25), na.rm = TRUE)
rel_qual <- rel_qual %>%
  select(ResponseId, dyadID, total_relation_qual)

gatekeep <- premeasures %>%
  select(ResponseId, dyadID, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15) %>%
  mutate_at(vars(-ResponseId, -dyadID), stripChars)

corr.test(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#looking good, nothing needs to be reversed

alpha(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15))
#.92 alpha, nothing that looks like it needs reversing

gatekeep$gatekeep_total <- rowMeans(select(gatekeep, gatekeeping_1, gatekeeping_4,  gatekeeping_6, gatekeeping_8, gatekeeping_10, gatekeeping_12, gatekeeping_14, gatekeeping_15), na.rm = TRUE)

gatekeep <- gatekeep %>% 
  select(ResponseId, dyadID, gatekeep_total)

scaleToNumeric <- function(x) {
  ifelse(x == "Strongly agree", 5, ifelse(x == "Somewhat agree", 4, ifelse(x == "Neither agree nor disagree", 3, ifelse(x == "Somewhat disagree", 2, ifelse(x == "Strongly disagree", 1, NA)))))
}

dd_gatekeep <- dailydiary %>%
  select(partID, dyadID, gate1, gate2, gate3, gate4, gate5, gate6) %>%
  mutate_at(vars(gate1, gate2, gate3, gate4, gate5, gate6), scaleToNumeric)

corr.test(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#no negative correlations again! we good.

alpha(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6))
#alpha of 0.84. Just fine. 1 and 4 could get dropped but it's consistent enough as is. 

dd_gatekeep$gateTotal <- rowMeans(select(dd_gatekeep, gate1, gate2, gate3, gate4, gate5, gate6), na.rm = TRUE)
dd_gatekeep <- dd_gatekeep %>%
  group_by(partID) %>%
  summarize(dd_gateTotal = mean(gateTotal))

assembled_dataset <- premeasures %>%
  select(ResponseId, dyadID, gender, race, Q139) %>%
  inner_join(., objectification) %>%
  inner_join(., rel_qual) %>%
  rename(relation_qual = total_relation_qual) %>%
  left_join(., gatekeep) %>%
  rename(gatekeep_premeasures = gatekeep_total) %>%
  left_join(dd_gatekeep, by = c("ResponseId" = "partID")) %>%
  rename(gatekeep_diaries = dd_gateTotal) %>%
  left_join(chores_final, by = c("ResponseId" = "partID")) %>%
  rename(childcare_tasks = total_chores) %>%
  left_join(filter_children) %>%
  rename(children_any = children) %>%
  rename(teleworking = Q139)

#cleanup
rm(objectification, rel_qual, gatekeep, dd_gatekeep, chores_final, filter_children)

total_childcare_temp <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  group_by(dyadID) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  summarize(total_tasks = sum(childcare_tasks)) %>%
  filter(total_tasks > 0)

childcare_temp2 <- assembled_dataset %>%
  select(ResponseId, dyadID, childcare_tasks) %>%
  left_join(total_childcare_temp) %>%
  filter(total_tasks > 0) %>%
  mutate(childcare_tasks = ifelse(is.na(childcare_tasks), 0, childcare_tasks)) %>%
  mutate(childcare_percent = childcare_tasks / total_tasks * 100) %>%
  select(ResponseId, childcare_percent)

assembled_dataset <- assembled_dataset %>%
  left_join(childcare_temp2)

#cleanup
rm(total_childcare_temp, childcare_temp2)

#Initial Corrections: 
#The number of children entered by R_3Jgt1VbMKwbyTKE seems to be a typo, entered 10, partner put 0. 
assembled_dataset <- assembled_dataset %>%
  mutate(childnum = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, childnum), children_any = ifelse(ResponseId == "R_3Jgt1VbMKwbyTKE", 0, children_any))


children <- assembled_dataset %>%
  select(ResponseId, dyadID, children_any, childnum) %>%
  group_by(dyadID)

maxchildren <- children %>%
  summarize(children_max = max(childnum))

children_discrep <- children %>%
  left_join(maxchildren) %>%
  mutate(child_diff = children_max - childnum) %>%
  filter(child_diff > 0)
#there were 18 respondents who reported fewer children than their partners. 

rm(maxchildren, children)

same_sex <- assembled_dataset %>%
  mutate(gender = ifelse(gender == "Man", 0, 1)) %>%
  group_by(dyadID) %>%
  summarize(couple = sum(gender)) %>%
  mutate(couple = ifelse(couple == 0, "Same-sex Male", ifelse(couple == 1, "Different-sex", "Same-sex Female")))
assembled_dataset <- assembled_dataset %>%
  left_join(same_sex, by = "dyadID") %>%
  rename(couple_genders = couple)


same_race <- assembled_dataset %>%
  group_by(dyadID, race) %>%
  summarize(n = n()) %>%
  mutate(couple_race = ifelse(n == 2, "Same Race", "Mixed Race")) %>%
  select(dyadID, couple_race) %>%
  distinct()
assembled_dataset <- assembled_dataset %>%
  left_join(same_race, by = c("dyadID" = "dyadID"))

```

# Measures:

#  Participants:


```{r}
same_sex <- assembled_dataset %>%
  mutate(gender = ifelse(gender == "Man", 0, 1)) %>%
  group_by(dyadID) %>%
  summarize(couple = sum(gender)) %>%
  mutate(couple = ifelse(couple == 0, "Same-sex Male", ifelse(couple == 1, "Different-sex", "Same-sex Female")))
```


```{r}
demographics<-premeasures %>%
  full_join(same_sex)%>%
  full_join(assembled_dataset)%>%
 select(dyadID,indinc, birthday,couple,childnum,Q138,gender,race,wfh)

```

```{r}
#premeasures %>%
#as.period(interval(start = relation_length, end = "4/2/2020"),unit="years")
```


```{r warning=FALSE}
tally( ~ Q138, data = demographics, format='percent')
```

```{r}
tally( ~ gender, data = demographics, format='percent')
```

```{r}
tally( ~ race, data = demographics, format='percent')
```

```{r}
tally( ~ wfh, data = demographics, format='percent')
```

```{r}
tally( ~ couple, data = demographics)
```


```{r}
tally( ~ couple, data = demographics, format='percent')
```

```{r}
favstats(~ indinc, data = premeasures)
favstats(~ birthday, data = premeasures)
favstats(~ childnum, data = assembled_dataset)
```


```{r}
destats<-demographics %>%
  select(indinc,birthday,childnum)
library(psych)
describe(destats)
```

The current study includes 182 couples where 172 are heterosexual couples, 7 are same-sex female and 3 are same-sex male. The majority of the sample were married (91.8%) and  8.2% were not married but in a committed relationship.  not married. The majority of the sample was white (74%), 10% identified as Asian or Asian American, 6.6% as Black or African American, and 5.8% as Latinx or Hispanic. The majority of the couples reported working from home (61.5%) and 20% were working in person(the rest were either missing value or other). The average age for parents was 45.8(middle-age) with SD=8.35 and the average annual income was  76,618 with SD= 105704. The median was 60,000 showing that the couples were mostly middle class. Finally, the reported number of children was 1.34 but the variance was big across the couples with an SD= 2.17.


In our analysis we discarded participants who did not answer most of the questions or missed questions that are crucial to our analysis. Specifically for our first reasearch question we decided not to include the 7 same-sex female couples since  we were mostly focsused on the connection between childcare tasks and relationship quality for men. 

Overall there are 172 different-gender couples and 10 same-sex couples.


#more to do:
better table
ICC
t-p vals
relationship length 
same race/ diffrent race


# table/figure: 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
