---
title             : "Results and Analysis Strategy"
shorttitle        : "Results"

author: 
  - name          : "Angela Jauregui"
    # affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
  - name          : "Lauren Meyer"
    #affiliation   : "1"  
  - name          : "Syrine Matoussi"
    # affiliation   : "1"
    role:


affiliation:
  - id            : " "
    institution   : "Smith College"



abstract: | 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "paper-references.bib", "annotated.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---





# Results

```{r setup, include = FALSE}
library(papaja)
library(mosaic)
library(lubridate)
library(nlme)
r_refs("r-references.bib")
```


```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r include = FALSE, echo=FALSE}
library(tidyverse)
library(readr)
library(psych)
library(kableExtra)
assembled_dataset<- read_csv("assembled-dataset.csv")
```

```{r include = FALSE}
fathers<-subset(assembled_dataset, gender="Man")%>%
mutate(telework=ifelse(teleworking == c("Yes, I am teleworking but my partner is not", "We are both teleworking"), 1, 0)) #not this is an indicator of NOT teleworking
```

```{r include = FALSE}  
fathers<-fathers%>%
mutate(gatekeep_premeasures = gatekeep_premeasures - mean(fathers$gatekeep_premeasures, na.rm = TRUE))
```

```{r include = FALSE}
fathers_APIM<-fathers
```


```{r include = FALSE}
gk_temp_1 <- fathers_APIM%>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(gatekeep_P1 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P1)

gk_temp_2 <- fathers_APIM%>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(gatekeep_P2 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P2)

fathers_APIM<- fathers_APIM%>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(gk_temp_1, by = c("dyadID", "ind")) %>%
  left_join(gk_temp_2, by = c("dyadID", "ind")) %>%
  mutate(gatekeep_P = ifelse(is.na(gatekeep_P1), gatekeep_P2, gatekeep_P1)) %>%
  select(-ind, -gatekeep_P2, -gatekeep_P1) %>%
  rename(gatekeep_A = gatekeep_premeasures)

rm(gk_temp_1, gk_temp_2)
```

```{r include = FALSE}

mlm <- gls(relation_qual ~ childcare_tasks, 
           data = fathers,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

summary(mlm)
```


```{r include = FALSE}
fathers_APIM %>%
  summarise(mean = mean(gatekeep_P, na.rm=TRUE),
            min(gatekeep_P, na.rm = TRUE),
            max(gatekeep_P, na.rm = TRUE))

fathers_APIM<-subset(fathers_APIM, gender=="Man")
  
fathers_APIM <- fathers_APIM %>%
  mutate(gatekeep_P_low= gatekeep_P + 2.00497,
         gatekeep_P_high= gatekeep_P - 1.99503)
#Child_tasks effect for mean gatekeep_A and gatekeep_P (because we grand-mean centered)
mlm1 <- lm(relation_qual ~ childcare_tasks 
            + gatekeep_A + gatekeep_P 
            + childcare_tasks*gatekeep_A + childcare_tasks*gatekeep_P, 
           data = fathers_APIM,
           na.action = na.omit)

summary(mlm1)

#Child_tasks effect when gatekeep_P is low. "Low" is the minimum of the gatekeep_P variable. Gatekeep_A remains at the mean. 
mlm_low <- lm(relation_qual ~ childcare_tasks 
            + gatekeep_A + gatekeep_P_low 
            + childcare_tasks*gatekeep_A + childcare_tasks*gatekeep_P_low, 
           data = fathers_APIM,
           na.action = na.omit)

summary(mlm_low)

#Child_tasks effect when gatekeep_P is high. "High" is the minimum of the gatekeep_P variable. Gatekeep_A remains at the mean.
mlm_high <- lm(relation_qual ~ childcare_tasks 
            + gatekeep_A + gatekeep_P_high 
            + childcare_tasks*gatekeep_A + childcare_tasks*gatekeep_P_high, 
           data = fathers_APIM,
           na.action = na.omit)

summary(mlm_high)
```


## First Hypothesis  

Our first hypothesis stated that fathers who took on a greater share of childcare tasks would have less relationship satisfaction. Due to the small number of dyads in our dataset, we used multiple regression modeling. 
To arrive at our final model, we included the explanatory variable childcare tasks. Our moderating variables were actor’s gatekeeping and partner’s gatekeeping. We created a new variable called “high-gatekeeping” to separately measure individuals with higher levels of gatekeeping by centering gatekeeping at the mean and subtracting 1.99 (as suggested by Randi, we are unclear about why and how to report it). We used the Actor-Partner Interdependence Model [@Kenny] to measure the interaction between actor’s and partner’s high-gatekeeping and childcare. The APIM allowed us to account for the nonindependence that is often present in dyads.

## Second and Third Hypotheses

Our second and third hypotheses were as follows: that partners who objectified their partner more would take on a smaller role in caring for their children, and that people who objectified themselves more would be more likely to take on an increased load of childcare tasks. We used multilevel modeling and the APIM [@Kenny]. Because our participants were individuals within couples, the APIM allowed us to conduct statistical analyses as multilevel models with indistinguishable dyads to account for the nonindependence and shared variance. 
Our final model included partner’s partner-objectification and actor’s self-objectification as explanatory variables. Gender was used as a moderating variable and gatekeeping was used as a control variable. We also modeled the interaction between gender and partner’s partner-objectification. 
During exploratory analysis we tested for actor’s partner-objectification, the moderation of race, ambivalent sexism (both actor and partner) and teleworking status, and several interaction terms. For parsimony, the model was then pared down to only include variables that were significant or nearing significance ($p$ $\leq$ 0.10). Although actor’s partner-objectification was a main explanatory variable for our second hypothesis, it was so insignificant and had such a high error term that it was disrupting the coefficient terms for the rest of the model and had to be dropped, ($b$ = -0.28, $t$ = -0.58, $p$ = 0.561).

## Missing Data

Out of the 364 individuals (182 couples) who answered the questionnaire for the first part of the study, only 265 participated in the later daily diaries portion. Of those, only 147 individuals had children and only 142 (71 couples) still had partners in the study. Individuals who did not respond to any of the questions used in the model were excluded.





```{r q1table}
df <- read.table(text = 
"'Childcare Tasks'  0.006   0.005   0.27
'Gatekeeping Actor'  -0.56    0.32   0.08
'Gatekeeping Partner high'  -0.37    0.30   0.23
'Childcare Tasks x Gatekeeping Actor'  -0.004    0.004  0.27
'Childcare Tasks x Gatekeeping Partner High'  	0.003    0.003  0.31"
)
names(df) <- c("variable","coefficient"," SE ", "  p-value")
# kbl(df) 
# df%>%
#  kbl( caption = '<b>Relationship Between Predictors and Relationship Satisfaction</b>', format = 'html') %>%
#   kable_styling()


df <- printnum(df)

apa_table(
  df, 
  caption = "Relationship Between Predictors and Relationship Satisfaction.",
 # note = "This table was created with apa_table()",
  escape = TRUE
)
```


# Main Results:

## Childcare tasks on father’s relationship satisfaction

See Table\ \@ref(tab:q1table) for all of the estimates from our final model.
Contrary to our first hypothesis, father's childcare task load had no statistically significant effect on relationship satisfaction when actor’s gatekeeping was at the mean and partner's gatekeeping was high, ($b$  $\leq$ 0.01, $SE$ $\leq$ 0.01, $p$ = 0.27).  
When fathers did no childcare tasks, there was no statistically significant effect of either actor or partner gatekeeping on relationship satisfaction, ($b$ = -0.56, $SE$ = 0.32, $p$ = 0.08), ($b$ = -0.37, $SE$ = 0.30, $p$ = 0.23). Doing more childcare tasks did not have a significant effect on the interaction of actor gatekeeping and relationship satisfaction, ($b$  $\leq$ 0.01, $SE$  $\leq$ 0.01, $p$ = 0.27). Similarly, childcare task load did not have a statistically significantly effect on the interaction of partner's high-gatekeeping and relationship satisfaction, ($b$  $\leq$ 0.01, $SE$  $\leq$ 0.01, $p$ = 0.31)

## Objectification predicting childcare labor contribution 

See Table\ \@ref(tab:q23table) for the estimates for all coefficients from our final model. Contrary to our second hypothesis, there was no effect of actor’s partner-objectification on childcare task load, ($b$ = -0.28, $t$ = -0.58, $p$ = 0.561). As predicted by our third hypothesis, there was a statistically significant effect of partner’s self-objectification on childcare task load, ($b$ = .85, $t$ = 2.33, $p$ = .021), with individuals who objectified themselves doing more childcare tasks. There was not a significant effect of actor’s partner-objectification on childcare task load, ($b$ = .60, $t$ = 1.39, $p$ = .165). 
Gender had a significant effect on childcare task load, with women on average doing more tasks than men, holding all other variables constant, ($b$ = 14.96, $t$ = 2.37, $p$ = .019). There was a significant interaction between gender and actor’s partner-objectification in a direction contrary to expectations, with women whose partners objectified them more doing fewer tasks than those whose partners objectified them less ($b$ = -1.72, $t$ = -2.57, $p$ = 0.011).




\newpage

```{r include = FALSE}

assembled_dataset <- read_csv("assembled-dataset.csv")

```

```{r include = FALSE}
children_only <- assembled_dataset %>%
  filter(children_any == 1) %>%
  group_by(dyadID) %>%
  summarize(childcare_notNA = sum(childcare_tasks))

children_and_tasks <- assembled_dataset %>%
  left_join(children_only) %>%
  filter(!is.na(childcare_notNA)) %>%
  filter(children_any == 1) %>%
  mutate(gender = ifelse(gender == "Man,Cis gendered", "Man", gender)) %>%
  mutate(gender = ifelse(gender == "Woman,Cis gendered", "Woman", gender)) %>%
  mutate(telework=ifelse(teleworking == c("Yes, I am teleworking but my partner is not", "We are both teleworking"), 0, 1))
rm(children_only)


full_dyads <- children_and_tasks %>%
  group_by(dyadID) %>%
  summarize(n = n())

children_and_tasks <- children_and_tasks %>%
  mutate(gatekeep_premeasures = gatekeep_premeasures - mean(children_and_tasks$gatekeep_premeasures, na.rm = TRUE))

```

```{r include = FALSE}
Basic_Objectification <- gls(childcare_tasks ~ self_obj_score + gender + gender*other_obj_score_P,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

summary(Basic_Objectification)
#Women in general do more tasks than men. People who objectify themselves more do more tasks. Curiously, men whose partners objectify them more do more childcare tasks (though insignificant), and women whose partners objectify them more do fewer childcare tasks. 
```


```{r include = FALSE}
gk_temp_1 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(gatekeep_P1 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P1)

gk_temp_2 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(gatekeep_P2 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P2)

children_and_tasks <- children_and_tasks %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(gk_temp_1, by = c("dyadID", "ind")) %>%
  left_join(gk_temp_2, by = c("dyadID", "ind")) %>%
  mutate(gatekeep_P = ifelse(is.na(gatekeep_P1), gatekeep_P2, gatekeep_P1)) %>%
  select(-ind, -gatekeep_P2, -gatekeep_P1) %>%
  rename(gatekeep_A = gatekeep_premeasures)

rm(gk_temp_1, gk_temp_2)

```

```{r include = FALSE}
cc_temp_1 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(Childcare_P1 = childcare_tasks) %>%
  select(dyadID, ind, Childcare_P1)

cc_temp_2 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(Childcare_P2 = childcare_tasks) %>%
  select(dyadID, ind, Childcare_P2)

children_and_tasks <- children_and_tasks %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(cc_temp_1, by = c("dyadID", "ind")) %>%
  left_join(cc_temp_2, by = c("dyadID", "ind")) %>%
  mutate(childcare_tasks_P = ifelse(is.na(Childcare_P1), Childcare_P2, Childcare_P1)) %>%
  select(-ind, -Childcare_P2, -Childcare_P1) %>%
  rename(childcare_tasks_A = childcare_tasks)

rm(cc_temp_1, cc_temp_2)


```


```{r include = FALSE}
apim_final <- gls(childcare_tasks_A ~ self_obj_score + gender + gender*other_obj_score_P + gatekeep_A,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

coeffs <- coef(apim_final)
summarized <- summary(apim_final)
t_table <- summarized$tTable
t_table <- data.frame(t_table)
row.names(t_table) <- c("Intercept","Self Objectification Score", "Female Gender", "Recieved Partner Objectification", "Gatekeeping", "Recieved Partner Objectification * Female Gender")
t_table <- t_table %>%
  select(-Std.Error) %>%
  rename(B = Value,'t' = t.value, 'p' = p.value)
```

```{r test, include = FALSE}
a <- unname(coeffs)
b <- names(coeffs)
test <- data.frame(a, b)
t_table <- printnum(t_table)
```

```{r q23table}

apa_table(
  t_table, 
  caption = "Effect of Self-Objectification on Childcare Tasks",
  escape = TRUE
)

```
## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

\newpage


# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
