---
title             : "Results and Analysis Strategy"
shorttitle        : "Results"

author: 
  - name          : "Angela Jauregui"
    # affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
  - name          : "Lauren Meyer"
    #affiliation   : "1"  
  - name          : "Syrine Matoussi"
    # affiliation   : "1"
    role:


affiliation:
  - id            : " "
    institution   : "Smith College"



abstract: | 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "paper-references.bib", "annotated.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---





# Results

```{r setup, include = FALSE}
library(papaja)
library(mosaic)
library(lubridate)
library(nlme)
library(dplyr)
r_refs("r-references.bib")
```


```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r include = FALSE, echo=FALSE}
library(tidyverse)
library(readr)
library(psych)
library(kableExtra)
assembled_dataset<- read_csv("assembled-dataset.csv")
```

```{r include = FALSE}
fathers<-assembled_dataset%>%
mutate(gatekeep_premeasures = gatekeep_premeasures - mean(assembled_dataset$gatekeep_premeasures, na.rm = TRUE))
```


```{r include = FALSE}
gk_temp_1 <- fathers%>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(gatekeep_P1 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P1)

gk_temp_2 <- fathers%>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(gatekeep_P2 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P2)

fathers<- fathers%>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(gk_temp_1, by = c("dyadID", "ind")) %>%
  left_join(gk_temp_2, by = c("dyadID", "ind")) %>%
  mutate(gatekeep_P = ifelse(is.na(gatekeep_P1), gatekeep_P2, gatekeep_P1)) %>%
  select(-ind, -gatekeep_P2, -gatekeep_P1) %>%
  rename(gatekeep_A = gatekeep_premeasures)

rm(gk_temp_1, gk_temp_2)
```



```{r include = FALSE}
fathers <- fathers 
fathers<-subset(fathers, gender=="Man")
  
#Child_tasks effect for mean gatekeep_A and gatekeep_P (because we grand-mean centered)
mlm1 <- lm(relation_qual ~ childcare_tasks 
            + gatekeep_A + gatekeep_P 
            + childcare_tasks*gatekeep_A + childcare_tasks*gatekeep_P, 
           data = fathers,
           na.action = na.omit)

summary(mlm1)
```


## First Hypothesis  

Our first hypothesis stated that fathers who took on a greater share of childcare tasks would have less relationship satisfaction. Due to the small number of same-sex male dyads in our dataset, we used multiple regression modeling with a non-dyadic dataset, only including men. To arrive at our final regression model, we included childcare tasks as a predictor and actor’s gatekeeping and partner’s gatekeeping as moderators.
## Second and Third Hypotheses

Our second and third hypotheses were as follows: that partners who objectified their partner more would take on a smaller role in caring for their children, and that people who objectified themselves more would be more likely to take on an increased load of childcare tasks. We used multilevel modeling and the APIM [@Kenny]. Because our participants were individuals within couples, the APIM allowed us to conduct statistical analyses as multilevel models with indistinguishable dyads to account for the nonindependence and shared variance. 
Our final model included partner’s partner-objectification and actor’s self-objectification as explanatory variables for the actor's childcare task load. Gender was used as a moderating variable and gatekeeping was used as a control variable. We also modeled the interaction between gender and partner’s partner-objectification. 
During exploratory analysis we tested for actor’s partner-objectification, the moderation of race, ambivalent sexism (both actor and partner) and teleworking status, and several interaction terms. For parsimony, the model was then pared down to only include variables that were significant or nearing significance ($p$ $\leq$ 0.10). Although actor’s partner-objectification was a main explanatory variable for our second hypothesis, it had such a high error term that it was disrupting the coefficient terms for the rest of the model and was thus dropped, ($b$ = -0.28, $t$ = -0.58, $p$ = 0.561).

## Missing Data

Out of the 364 individuals (182 couples) who answered the questionnaire for the first part of the study, only 265 participated in the later daily diaries portion. Of those, only 147 individuals had children and only 142 (71 couples) still had partners in the study. Individuals who did not respond to any of the questions used in the model were excluded.





```{r q1table}
df <- read.table(text = 
"'Childcare Tasks'  '< 0.01'   '< 0.01'   0.94
'Gatekeeping Actor'  -0.56    0.32   0.08
'Gatekeeping Partner high'  -0.37    0.30   0.23
'Childcare Tasks x Gatekeeping Actor'  '< 0.01'    '< 0.01'  0.27
'Childcare Tasks x Gatekeeping Partner'  '< 0.01'  '< 0.01'  0.31"
)
names(df) <- c("variable","coefficient"," SE ", "  p-value")
# kbl(df) 
# df%>%
#  kbl( caption = '<b>Relationship Between Predictors and Relationship Satisfaction</b>', format = 'html') %>%
#   kable_styling()


df <- printnum(df)

apa_table(
  df, 
  caption = "Relationship Between Predictors and Relationship Satisfaction.",
 # note = "This table was created with apa_table()",
  escape = TRUE
)
```


# Main Results

## Childcare tasks on father’s relationship satisfaction

See Table\ \@ref(tab:q1table) for all of the estimates from our final model.
Contrary to our first hypothesis, father's childcare task load had no statistically significant effect on relationship satisfaction when actor’s and partner's gatekeeping was at the mean ($b$  $\leq$ 0.01, $SE$ $\leq$ 0.01, $p$ = 0.94).  
When fathers did no childcare tasks, there was no statistically significant effect of either actor's or partner's gatekeeping on relationship satisfaction, ($b$ = -0.56, $SE$ = 0.32, $p$ = 0.08), ($b$ = -0.37, $SE$ = 0.30, $p$ = 0.23). The interaction between performing more childcare tasks and actor's gatekeeping did not have a significant effect on relationship satisfaction for fathers, ($b$  $\leq$ 0.01, $SE$  $\leq$ 0.01, $p$ = 0.27). Similarly, the interaction between performing more childcare tasks and partner's gatekeeping did not have a significant effect on relationship satisfaction for fathers, ($b$  $\leq$ 0.01, $SE$  $\leq$ 0.01, $p$ = 0.31)

## Objectification predicting childcare labor contribution 

See Table\ \@ref(tab:q23table) for the estimates for all coefficients from our final model. Contrary to our second hypothesis, there was no effect of actor’s partner-objectification on childcare task load, ($b$ = -0.28, $t$ = -0.58, $p$ = 0.561). As predicted by our third hypothesis, there was a statistically significant effect of actor’s self-objectification on childcare task load, ($b$ = .85, $t$ = 2.33, $p$ = .021), with individuals who objectified themselves doing more childcare tasks. There was no significant effect of the actor's objectification of their partner on childcare task load, ($b$ = .60, $t$ = 1.39, $p$ = .165). 
Gender had a significant effect on childcare task load, with women on average doing more tasks than men, ($b$ = 14.96, $t$ = 2.37, $p$ = .019). There was a significant interaction between gender and partner’s partner-objectification in a direction contrary to expectations, with women whose partners objectified them more doing fewer tasks than those whose partners objectified them less ($b$ = -1.72, $t$ = -2.57, $p$ = 0.011).




\newpage

```{r include = FALSE}

assembled_dataset <- read_csv("assembled-dataset.csv")

```

```{r include = FALSE}
children_only <- assembled_dataset %>%
  filter(children_any == 1) %>%
  group_by(dyadID) %>%
  summarize(childcare_notNA = sum(childcare_tasks))

children_and_tasks <- assembled_dataset %>%
  left_join(children_only) %>%
  filter(!is.na(childcare_notNA)) %>%
  filter(children_any == 1) %>%
  mutate(gender = ifelse(gender == "Man,Cis gendered", "Man", gender)) %>%
  mutate(gender = ifelse(gender == "Woman,Cis gendered", "Woman", gender)) %>%
  mutate(telework=ifelse(teleworking == c("Yes, I am teleworking but my partner is not", "We are both teleworking"), 0, 1))
rm(children_only)


full_dyads <- children_and_tasks %>%
  group_by(dyadID) %>%
  summarize(n = n())

children_and_tasks <- children_and_tasks %>%
  mutate(gatekeep_premeasures = gatekeep_premeasures - mean(children_and_tasks$gatekeep_premeasures, na.rm = TRUE))

```

```{r include = FALSE}
Basic_Objectification <- gls(childcare_tasks ~ self_obj_score + gender + gender*other_obj_score_P,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

summary(Basic_Objectification)
#Women in general do more tasks than men. People who objectify themselves more do more tasks. Curiously, men whose partners objectify them more do more childcare tasks (though insignificant), and women whose partners objectify them more do fewer childcare tasks. 
```


```{r include = FALSE}
gk_temp_1 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(gatekeep_P1 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P1)

gk_temp_2 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(gatekeep_P2 = gatekeep_premeasures) %>%
  select(dyadID, ind, gatekeep_P2)

children_and_tasks <- children_and_tasks %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(gk_temp_1, by = c("dyadID", "ind")) %>%
  left_join(gk_temp_2, by = c("dyadID", "ind")) %>%
  mutate(gatekeep_P = ifelse(is.na(gatekeep_P1), gatekeep_P2, gatekeep_P1)) %>%
  select(-ind, -gatekeep_P2, -gatekeep_P1) %>%
  rename(gatekeep_A = gatekeep_premeasures)

rm(gk_temp_1, gk_temp_2)

```

```{r include = FALSE}
cc_temp_1 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 0) %>%
  rename(Childcare_P1 = childcare_tasks) %>%
  select(dyadID, ind, Childcare_P1)

cc_temp_2 <- children_and_tasks %>%
  mutate(ind = rep(c(1, 0),length.out = n())) %>%
  group_by(dyadID) %>%
  filter(ind == 1) %>%
  rename(Childcare_P2 = childcare_tasks) %>%
  select(dyadID, ind, Childcare_P2)

children_and_tasks <- children_and_tasks %>%
  mutate(ind = rep(c(0, 1),length.out = n())) %>%
  left_join(cc_temp_1, by = c("dyadID", "ind")) %>%
  left_join(cc_temp_2, by = c("dyadID", "ind")) %>%
  mutate(childcare_tasks_P = ifelse(is.na(Childcare_P1), Childcare_P2, Childcare_P1)) %>%
  select(-ind, -Childcare_P2, -Childcare_P1) %>%
  rename(childcare_tasks_A = childcare_tasks)

rm(cc_temp_1, cc_temp_2)


```


```{r include = FALSE}
apim_final <- gls(childcare_tasks_A ~ self_obj_score + gender + gender*other_obj_score_P + gatekeep_A,
           data = children_and_tasks,
           correlation = corCompSymm(form=~1|dyadID),
           na.action = na.omit)

coeffs <- coef(apim_final)
summarized <- summary(apim_final)
t_table <- summarized$tTable
t_table <- data.frame(t_table)
row.names(t_table) <- c("Intercept","Self Objectification Score", "Female Gender", "Partner's Partner Objectification", "Gatekeeping", "Partner's Partner Objectification * Female Gender")
t_table <- t_table %>%
  select(-Std.Error) %>%
  rename(B = Value,'t' = t.value, 'p' = p.value)
```

```{r test, include = FALSE}
a <- unname(coeffs)
b <- names(coeffs)
test <- data.frame(a, b)
t_table <- printnum(t_table)
```

```{r q23table}

apa_table(
  t_table, 
  caption = "Effect of Self-Objectification on Childcare Tasks",
  escape = TRUE
)

```
## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

\newpage


# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
